---
title: "Analysis for the field survey of Paratemnoides nidificator activity"
author: "Laura Segura"
date: "21/Aug/2021"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
editor_options: 
  chunk_output_type: inline
---

Parking downhill: 
Redo binomial models: check if removing fandom factor is needed and select models
Do descriptive plots for corresponding models
Summarize results for Carola
Figure out analysis for quantity of individuals


Preguntas GB:
Si el glmm dice que isSingular: la varianza del factor aleatorio es muy poca, mejor quitar el factor aleatorio o no?
 aic debe diferir por mas de dos unidades, si tiene menos de dos unidades es lo mismo y se escge el mas sencilo. O hacer anova d los modelos


Preguntas en general:
Ejemplo de chelas afuera todas las colonias: si la variable tiempo era parte de mi pregunta, pero al final el model dice que da lo mismo incluirla que excluirla (o sea, la variable realmente no esta ayudando a explicar nada en el modelo), cual dejo como modelo final? 

Para tomar en cuenta el tiempo: es mejor usar tiempo como una variable continua (minutos del dia, hora del dia), discreta (agrupandolos por hora) o categorica (hora)


```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
#chunk_output_type: inline
```
# Loading the libraries

```{r}
library(tidyr)
library(dplyr)
library(lubridate)
library(survival)
library(ggplot2)
library(forcats)
library(survminer)
library(emmeans)
library(googlesheets4)
library(forcats)
library(scales)
library(ggridges)
library(NRES803)
library(MASS)
library(RColorBrewer)
library(nlme)
library(gridExtra)
library(pscl)
library(glmmADMB)
library(ordinal)
library(purrr)
library(lme4)
library(sjPlot)
library(mclogit)
library(pander)
library(MuMIn)
library(AICcmodavg)
library(broom)
library(DHARMa)
library(statmod)
library(broom.mixed)
library(grid)
```

# Getting data 

## Signing up to my google account and getting the data sheet

I just need to run this line to give access to my google account to tidy verse to be able to work on the google sheet more easily

```{r, message=FALSE}
gs4_auth(email="laurasegura.bio@gmail.com")

```

```{r}
data1<-read_sheet('https://docs.google.com/spreadsheets/d/1A8WTomc5c3l5xX3ZSnJoAV-uPuUVoim1g9wf6VQqkss/edit?gid=0#gid=0', sheet="Environmental info", na = c("", "NA","NULL", NULL))

data2<-read_sheet('https://docs.google.com/spreadsheets/d/1A8WTomc5c3l5xX3ZSnJoAV-uPuUVoim1g9wf6VQqkss/edit?gid=0#gid=0', sheet="ActJunio", na = c("", "NA","NULL", NULL))
#Removing the first 3 example rows and the rows observations not part of the census, but extra info from the colony size census
data1<-data1[-c(1:3),]


#Removing the first 3 example rows and the rows observations not part of the census, but extra info from the colony size census
data1<-data1[-c(1:3),]


data<-bind_rows(data1,data2)%>%
  mutate(colony=as.factor(Colonia),
         date=ymd(Fecha),
         location=as.factor(Location),
         time2=format(as.POSIXct(Hora), format="%H:%M"),
         time=hm(time2),
         day=ymd(Day),
         t.amb=as.numeric(Temp_amb),
         h.amb=as.numeric(Hum_amb),
         t1=as.numeric(`Temp_1 (con_pseudos)`),
         t2=as.numeric(`Temp_2_(con_pseudos)`),
         t.pseudos=(t1+t2)/2,
         t3=as.numeric(`Temp_3(sin_pseudos)`),
         t4=as.numeric(`Temp_4_(sin_pseudos)`),
         t.nopseudos=(t3+t4)/2,
         t.tree=(t1+t2+t3+t4)/4,
         rain=factor(Ult_lluvia, levels=c("Recent", "Afternoon","Morning", "1Day","2Days" )),
         raindate=ymd(Fecha_ult_lluvia),
         raintime=format(as.POSIXct(Hora_ult_lluvia), format="%H:%M"),
         raintime2=hm(raintime),
         luna=as.factor(Luna),
         phase=factor(Fase_lunar,levels=c("NM","CM", "FM", "WM")),
         mlight=as.factor(Luz_luna),
         sky=as.factor(Cielo),
         bark=factor(Corteza, levels=c("Dry","Moist", "Wet", "NA")),
         can.cov=factor(Cobertura, levels=c("Low","Medium", "High", "NA")),
         mosss=as.factor(Musgo),
         vis=as.factor(Visibilidad),
         act=as.factor(Escala_actividad), 
         act2=as.numeric(Escala_actividad),
         pq=Q/total,
         pc=C/total,
         pa=A/total,
         ps=S/total,
         pe=E/total,
         pf=F/total, 
         hour=hour(time),
         hour2=factor(hour,levels=c("20","21", "22", "23", "0", "1", "2", "3", "4")),
         act3=ceiling(act2),
          act4=as.factor(act3)
         ) %>%
  filter(Census=="census")
  
  
data<-dplyr::select(data, -c(Colonia, Location, Day, Temp_amb, Hum_amb,`Temp_1 (con_pseudos)`, `Temp_2_(con_pseudos)`,`Temp_3(sin_pseudos)`, `Temp_4_(sin_pseudos)`, Luna, Fase_lunar, Visibilidad, Escala_actividad,  Ult_lluvia, Ultima_lluvia, Luz_luna, Fecha_ult_lluvia, Hora_ult_lluvia,Cielo, Obs_cobertura, Cobertura, Musgo, Presas_ID,num_parasitos, Actividad_parasitos,Actividad_colonia, Otras_observaciones, Census  )) 
  
 # select(=c(colony, location, date,day,time,time2, t.amb,h.amb, t.pseudos, t.nopseudos,t.tree, luna, phase, vis, Presas_ID, Presas_frecuencia, act, act2))

data$daytime<-as.POSIXct(paste(data$day, data$time2), format="%Y-%m-%d %H:%M")
data$obsdaytime<-as.POSIXct(paste(data$date, data$time2), format="%Y-%m-%d %H:%M")
data$raindaytime<-as.POSIXct(paste(data$raindate, data$raintime), format="%Y-%m-%d %H:%M")
data$rainpassed<- data$obsdaytime-data$raindaytime 
data$rainpassed2<-difftime(data$obsdaytime,data$raindaytime, units="hours")         

 


str(data)



        

data2<-data%>%
  drop_na(act) %>%
  filter(location!="Laguna",
         hour>19) # OJo: aca esta filtrando por las horas para que solo sea todo antes de la media noche
         

data3<-data%>%
  drop_na(act) %>%
  filter(location!="Laguna")
        
```

# Questions

1. How does activity vary with hour (time)?
How does activity vary between locations?
2. How does activity vary with ambient temperature?
3. How does activity vary with ambient humidity?
4. How does activity vary with temperature at the crevice?
5. Are the temperatures of the occupied crevices different to the non-occupied ones?
6. How does activity vary with overall tree temperautre?
7. How does activity vary with lunar condition?
8. How does activity vary with lunar phase?
9. What are the most common prey items?
10.Do predation events vary with ambient temperature?
11. Do predation events vary with humidity?

# Looking at arthropods associated
```{r}
dataart<-read_sheet('https://docs.google.com/spreadsheets/d/1A8WTomc5c3l5xX3ZSnJoAV-uPuUVoim1g9wf6VQqkss/edit?gid=0#gid=0', sheet="Arthropods_associated", na = c("", "NA","NULL", NULL))


dataart<-dataart %>% filter(date>="2025-05-01",
                            Artropodo_orden!="REVISAR") %>% 
  dplyr::select(c(colony, date, hour, location, Artropodo_orden, Artropodo_frecuencia, Cerca_de_colonia)) %>%
  mutate(colony=as.factor(colony),
         location=as.factor(location),
         ord=as.factor(Artropodo_orden),
         freq=as.numeric(Artropodo_frecuencia),
         cerca=as.factor(Cerca_de_colonia)) 

str(dataart)
levels(dataart$ord)
```

## Plotting artropods on colonies
```{r}
dataart %>% group_by(ord) %>%
  summarize(total=sum(freq)) %>% 
  arrange(desc(total)) %>%
  ggplot(aes(x=ord, y=total))+geom_bar(stat="identity") + theme_classic()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + ylab("Frecuency") + xlab("Order")
ggsave("Plots/arthropods_all.png", plot = last_plot(), width=6, heigh=4, units="in")

dataart %>% group_by(ord) %>%
  summarize(total=sum(freq)) %>% 
  arrange(desc(total))

dataart %>% group_by(location,ord) %>%
  summarize(total=sum(freq)) %>%
  ggplot(aes(x=ord, y=total))+geom_bar(stat="identity") + theme_classic()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + ylab("Frecuency") + xlab("Order") + facet_wrap(~location, nrow=3)
ggsave("Plots/arthropods_location.png", plot = last_plot(), width=6, heigh=4, units="in")

dataart %>% group_by(location,ord) %>%
  summarize(total=sum(freq)) %>% 
  arrange(desc(total))


```
## Plotting only nearby artropods on colonies
```{r}
dataart %>% filter(cerca=="si") %>% group_by(ord) %>%
  summarize(total=sum(freq)) %>% 
  arrange(desc(total)) %>%
  ggplot(aes(x=ord, y=total))+geom_bar(stat="identity") + theme_classic()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + ylab("Frecuency") + xlab("Order")
ggsave("Plots/Nearby_all.png", plot = last_plot(), width=6, heigh=4, units="in")

dataart %>% filter(cerca=="si") %>%group_by(ord) %>%
  summarize(total=sum(freq)) %>% 
  arrange(desc(total))

dataart %>%filter(cerca=="si") %>% group_by(location,ord) %>%
  summarize(total=sum(freq)) %>%
  ggplot(aes(x=ord, y=total))+geom_bar(stat="identity") + theme_classic()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + ylab("Frecuency") + xlab("Order") + facet_wrap(~location, nrow=3)
ggsave("Plots/Nearby_location.png", plot = last_plot(), width=6, heigh=4, units="in")

dataart %>% filter(cerca=="si") %>%group_by(location,ord) %>%
  summarize(total=sum(freq)) %>% 
  arrange(desc(total))


```
## Plotting only prey
```{r}
data2<-data2 %>% mutate(presas=as.factor(Presas_ID2))
levels(data2$presas)

data2 %>% drop_na(presas) %>% group_by(presas) %>%
  summarize(total=sum(Presas_frecuencia)) %>% 
  arrange(desc(total)) %>%
  ggplot(aes(x=presas, y=total))+geom_bar(stat="identity") + theme_classic()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + ylab("Frecuency") + xlab("Prey")
ggsave("Plots/Prey_all.png", plot = last_plot(), width=6, heigh=4, units="in")

data2 %>% drop_na(presas) %>% group_by(presas) %>%
  summarize(total=sum(Presas_frecuencia)) %>% 
  arrange(desc(total))

data2 %>% drop_na(presas) %>% group_by(location,presas) %>%
  summarize(total=sum(Presas_frecuencia)) %>%
  ggplot(aes(x=presas, y=total))+geom_bar(stat="identity") + theme_classic()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + ylab("Frecuency") + xlab("Order") + facet_wrap(~location, nrow=3)
ggsave("Plots/Prey_location.png", plot = last_plot(), width=6, heigh=4, units="in")

data2 %>% drop_na(presas) %>% group_by(location,presas) %>%
  summarize(total=sum(Presas_frecuencia)) %>% 
  arrange(desc(total))


```



# Checking variation of environmental variables per colony
## Time
```{r}
# All data
ggplot(data3, aes(y=daytime, x=colony))+geom_boxplot()+ geom_jitter(color="red", alpha=0.5)+ ylab("Time") + xlab(" ")+theme_classic() 

# Cutting BCI data to just 8 to 12
ggplot(data2, aes(y=daytime, x=colony))+geom_boxplot()+ geom_jitter(color="red", alpha=0.5)+ ylab("Time") + xlab(" ")+theme_classic()

```

## Temperatures
```{r}

## T.amb
# All data
ggplot(data3, aes(y=t.amb, x=colony))+geom_boxplot()+ geom_jitter(color="red", alpha=0.5)+ ylab("T. amb") + xlab(" ")+theme_classic() 

# Cutting BCI data to just 8 to 12
ggplot(data2, aes(y=t.amb, x=colony))+geom_boxplot()+ geom_jitter(color="red", alpha=0.5)+ ylab("T.amb") + xlab(" ")+theme_classic()

## t.pseudos
# All data
ggplot(data3, aes(y=t.pseudos, x=colony))+geom_boxplot()+ geom_jitter(color="red", alpha=0.5)+ ylab("T.pseudos") + xlab(" ")+theme_classic() 

# Cutting BCI data to just 8 to 12
ggplot(data2, aes(y=t.pseudos, x=colony))+geom_boxplot()+ geom_jitter(color="red", alpha=0.5)+ ylab("T.pseudos") + xlab(" ")+theme_classic()

## t.pseudos
# All data
ggplot(data3, aes(y=t.tree, x=colony))+geom_boxplot()+ geom_jitter(color="red", alpha=0.5)+ ylab("T.tree") + xlab(" ")+theme_classic() 

# Cutting BCI data to just 8 to 12
ggplot(data2, aes(y=t.tree, x=colony))+geom_boxplot()+ geom_jitter(color="red", alpha=0.5)+ ylab("T.tree") + xlab(" ")+theme_classic()

```

## Humidity
```{r}
# All data
ggplot(data3, aes(y=h.amb, x=colony))+geom_boxplot()+ geom_jitter(color="red", alpha=0.5)+ ylab("H. amb") + xlab(" ")+theme_classic() 

# Cutting BCI data to just 8 to 12
ggplot(data2, aes(y=h.amb, x=colony))+geom_boxplot()+ geom_jitter(color="red", alpha=0.5)+ ylab("H.amb") + xlab(" ")+theme_classic()
```

## Rain
```{r}
# All data
ggplot(data3, aes(y=raintime2, x=colony))+geom_boxplot()+ geom_jitter(color="red", alpha=0.5)+ ylab("Raintime") + xlab(" ")+theme_classic() 

# Cutting BCI data to just 8 to 12
ggplot(data2, aes(y=raintime2, x=colony))+geom_boxplot()+ geom_jitter(color="red", alpha=0.5)+ ylab("Raintime") + xlab(" ")+theme_classic()
```



## Light, moonphase and sky conditions
```{r}
## Luna
# All data
ggplot(data3, aes(x=colony))+geom_bar()+ ylab("Luna") + xlab(" ")+theme_classic()+ facet_wrap(~luna) 

# Cutting BCI data to just 8 to 12
ggplot(data2, aes(x=colony))+geom_bar()+ ylab("Luna") + xlab(" ")+theme_classic()+ facet_wrap(~luna) 

## Phase
ggplot(data3, aes(x=phase))+geom_bar()+ ylab("Luna") + xlab(" ")+theme_classic()+ facet_wrap(~colony) 

# Cutting BCI data to just 8 to 12
ggplot(data2, aes(x=phase))+geom_bar()+ ylab("Luna") + xlab(" ")+theme_classic()+ facet_wrap(~colony) 

## mlight
ggplot(data3, aes(x=mlight))+geom_bar()+ ylab("Luna") + xlab(" ")+theme_classic()+ facet_wrap(~colony) 

# Cutting BCI data to just 8 to 12
ggplot(data2, aes(x=mlight))+geom_bar()+ ylab("Luna") + xlab(" ")+theme_classic()+ facet_wrap(~colony) 

## sky
ggplot(data3, aes(x=sky))+geom_bar()+ ylab("Luna") + xlab(" ")+theme_classic()+ facet_wrap(~colony) 

# Cutting BCI data to just 8 to 12
ggplot(data2, aes(x=sky))+geom_bar()+ ylab("Luna") + xlab(" ")+theme_classic()+ facet_wrap(~colony)
```


## Bark, moss, canopy
```{r}
## Bark
# All data
ggplot(data3, aes(x=bark))+geom_bar()+ ylab("Bark") + xlab(" ")+theme_classic()+ facet_wrap(~colony) 

# Cutting BCI data to just 8 to 12
ggplot(data2, aes(x=bark))+geom_bar()+ ylab("Bark") + xlab(" ")+theme_classic()+ facet_wrap(~colony)

## Canopy coverage
# All data
ggplot(data3, aes(x=can.cov))+geom_bar()+ ylab("Canopy coverage") + xlab(" ")+theme_classic()+ facet_wrap(~colony) 

# Cutting BCI data to just 8 to 12
ggplot(data2, aes(x=can.cov))+geom_bar()+ ylab("Canopy coverage") + xlab(" ")+theme_classic()+ facet_wrap(~colony)

## Moss
# All data
ggplot(data3, aes(x=mosss))+geom_bar()+ ylab("Moss") + xlab(" ")+theme_classic()+ facet_wrap(~colony) 

# Cutting BCI data to just 8 to 12
ggplot(data2, aes(x=mosss))+geom_bar()+ ylab("Moss") + xlab(" ")+theme_classic()+ facet_wrap(~colony)

```



# Checking temperature correlations

## How close are the tree temp and the ambient temperature? Are they correlated?
```{r}
temp<-data3%>%filter(date<"2025-06-01") %>%
  mutate(diff=t.amb-t.pseudos) %>%
  drop_na(act) %>%
  drop_na(diff)%>%
  filter(location!="Laguna")


temp%>%
  ggplot(aes(y=diff, x="")) +geom_boxplot() + geom_jitter()+ ylab("Difference") + xlab(" ")+theme_classic()
ggsave("Plots/tempsdiff.png", plot = last_plot(), width=6, heigh=4, units="in")

mean(abs(temp$diff))
sd(abs(temp$diff))

summary(lm(data=temp, t.pseudos~t.amb))
ggplot(data=temp, aes(x=t.amb, y=t.pseudos))+geom_point()+geom_smooth(method="lm")

shapiro.test(temp$t.amb) #T.amb not normal
shapiro.test(temp$t.pseudos) # t. pseudos is normal

#Data not normal, therefore, I should use the Pearson correlation test
cor.test(temp$t.amb, temp$t.pseudos, method="pearson")

#there is a correlation between the ambient temp and the temp of the occupied crevices

```

There is a correlation between the ambient temp and the temp of the occupied crevices


## Are temperature and humidity correlated?
```{r}
shapiro.test(data3$t.amb)
shapiro.test(data3$h.amb)

#Data is not normal, therefore, I should use the Spearman correlation test
cor.test(data3$t.amb, data3$h.amb, method="spearman")


ggplot(data2, aes(y=t.amb, x=h.amb))+geom_point() +geom_smooth(method="lm") + ylab("Temperature (°C)") + xlab("Humidity (%)")+theme_classic()
ggsave("Plots/temps-humrel.png", plot = last_plot(), width=6, heigh=4, units="in")


```

There is a negative correlation between ambient temperature and ambien humidity

## Are temperature and hour correlated?
```{r}

#Data is not normal, therefore, I should use the Spearman correlation test
cor.test(data3$t.amb, data3$time, method="spearman")


ggplot(data3, aes(y=t.amb, x=daytime))+geom_point() +geom_smooth(method="lm") + ylab("Temperature (°C)") + xlab("Time of day")+theme_classic()
ggsave("Plots/temps-time.png", plot = last_plot(), width=6, heigh=4, units="in")

#Data is not normal, therefore, I should use the Spearman correlation test
cor.test(data3$t.amb, data3$hour, method="spearman")


ggplot(data3, aes(y=t.amb, x=hour))+geom_point() +geom_smooth(method="lm") + ylab("Temperature (°C)") + xlab("Time of day")+theme_classic()
ggsave("Plots/temps-hour.png", plot = last_plot(), width=6, heigh=4, units="in")



```
No hay correlacion entre hora y temperatura




# Examining each behavior instead of the activity scale

## PRESENCE/ABSENCE of each behavior: All colonies between 8pm and 12 midnight

### Organizing the data
```{r}

# Total number of pseudoscorpions doing the activity
databin<-data2 %>%  
  #dplyr::select(colony, location,t.amb, h.amb, phase, time, daytime, hour, Q, C, A, S, E, F, total) %>%
  pivot_longer(cols=(7:12), names_to = "beh" , values_to="inds") %>%
  mutate(prop=inds/total, 
         hour2=factor(hour,levels=c("20","21", "22", "23", "0", "1", "2", "3", "4")),
         bin=if_else(inds>0,1,0),
         beh2=case_when(beh=="A"~"Feeding",
                        beh=="C"~"Outside",
                        beh=="E"~"Hiding",
                        beh=="F"~"Outside",
                        beh=="Q"~"Chelaes exp.",
                        beh=="S"~"Peeking out",
                        TRUE~NA),
         timesec=as.numeric(time),
         timemin=(as.numeric(time))/60,
         halfhour=case_when(between(timemin, 1200,1230)~"20:30",
                                  between(timemin, 1231,1260)~"21:00", 
                                  between(timemin, 1261,1290)~"21:30",
                                  between(timemin, 1291,1320)~"22:00",
                                  between(timemin, 1321,1350)~"22:30",
                                  between(timemin, 1351,1380)~"23:00",
                                  between(timemin, 1381,1410)~"23:30",
                                  between(timemin, 1411,1440)~"24:00",
                                  TRUE~NA),
         tempb=case_when(between(t.amb, 23.8,24.5)~"24.5",
                         between(t.amb, 24.5, 25.0)~"25",
                         between(t.amb, 25.0, 25.5)~"25.5",
                         between(t.amb, 25.5, 26.0)~"26",
                         between(t.amb, 26.0, 26.5)~"26.5",
                         between(t.amb, 26.5, 27.0)~"27",
                         between(t.amb, 27.0, 27.5)~"27.5",
                         between(t.amb, 27.5, 28.0)~"28",
                         TRUE~NA))
mr<-min(databin$rainpassed2)
mb<-mr-mr
databin<-databin%>%mutate(rainb=case_when(between(rainpassed2, mb,mb+2) ~"0-2",
                         between(rainpassed2, mb+2,mb+6)~"2-6",
                         between(rainpassed2, mb+6, mb+12)~"6-12",
                         between(rainpassed2, mb+12, mb+18)~"12-18",
                         between(rainpassed2, mb+18, mb+24)~"18-24",
                         between(rainpassed2, mb+24, mb+30)~"24-30",
                         between(rainpassed2, mb+30, mb+36)~"30-36",
                         between(rainpassed2, mb+36, mb+42)~"36-42",
                         between(rainpassed2, mb+42, mb+48)~"42-48",
                         between(rainpassed2, mb+48, mb+57)~"48+",
                         TRUE~NA)
  )

databin$rainb<-factor(databin$rainb,levels=c("0-2","2-6", "6-12", "12-18", "18-24", "24-30", "30-36", "36-42", "42-48",  "48+"))         

databin$beh2<-factor(databin$beh2, levels=c("Peeking out", "Chelaes exp.", "Feeding", "Outside", "Hiding"))

databin<-databin %>%  dplyr::select(colony, timemin,obsdaytime,time,hour,  t.amb, rainpassed2, mlight, phase, bin, total, beh, beh2, halfhour, tempb, rainb)

#timesec has a huge value compared to the scale of the other values and the model is giving me a warning, so I will re-scale it by deducting the minimum timesec value and going from then onwards on time

levels(databin$rainb)
summary(databin)

```

### CHELAES EXPOSED
#### Determining the global model
```{r}
#Getting the dataset for just this behavior
chela<-databin%>%filter(beh=="Q")
sum(chela$bin)
nrow(chela)

b1<-glmer(bin~timemin+t.amb+rainpassed2+phase+(1|colony), data=chela, family=binomial)
summary(b1) # This model gives the isSingular warning: the colony random factor has a variance of zero, the odel is not detecting diferences between the colonies, so I can consider removing it and see which model is better

b2<-glm(bin~timemin+t.amb+rainpassed2+phase, data=chela, family=binomial) # same model as before but without the colony
summary(b2)

# Comparing the models with an anova
anova(b1,b2) # the models are identical: it is the same to include or exclude the random factor, so I will go with the simpler model, without the random factor

# Final model
b2<-glm(bin~timemin+t.amb+rainpassed2+phase, data=chela, family=binomial)
summary(b2)
```

#### Checking residuals of global model
```{r}
# Global model without the random factor (best model according to anova)
## Checking for overdispersion
summary(b2)
glanceb2<-glance(b2)
glanceb2
gofb2 <- with(glanceb2,pchisq(deviance,df.residual,lower=FALSE)) #creating the object that would allow to get the p-value
gofb2 #p-value to test overdispersion
#This model is not significantly overdispersed: X2= 161.18, df=152, p=0.29

## Plotting residuals for each variable
b2test <- augment(b2) #gets a dataframe with each value foe each variable, covariate, the residuals, fitted, std.resid, .hat, cook sd, etc
lin.time<- ggplot(b2test, aes(x = timemin, y = .std.resid)) + geom_count() + 
  scale_size_area(max_size=4) + 
  geom_hline(yintercept = 0, linetype = 2) + 
  geom_smooth() + guides(size = FALSE) 
#Creating the other graphs
lin.temp <- lin.time + aes(x = t.amb)
lin.rainpassed2 <- lin.time + aes(x = rainpassed2)
lin.phase <- lin.time + aes(x = phase)
#Putting all graphs together
grid.arrange(lin.time, lin.temp, lin.rainpassed2, lin.phase)

## Checking residuals in general
check_assumptions(b2)
t2<-simulateResiduals(b2)
plot(t2) 

## CONCLUSION: the model is robust enough, it is not overdispersed and the residuals look good


# Model with the random factor

summary(b1)
gofb1 <- pchisq(161.2,151,lower=FALSE) #creating the object that would allow to get the p-value
gofb1 #p-value to test overdispersion
#This model is not significantly overdispersed: X2= 161.18, df=151, p=0.27


b1<-glmer(bin~timemin+t.amb+rainpassed2+phase+(1|colony), data=chela, family=binomial)
summary(b1)
# Checking residuals
#check_assumptions(b1)
residb1 <- augment(b1)
qres.binom <- function(glmer.obj) {
    p <- fitted(glmer.obj)
    y <- glmer.obj@resp$y
    if (!is.null(glmer.obj@resp$weights)) 
        n <- glmer.obj@resp$weights else n <- rep(1, length(y))
    y <- n * y
    a <- pbinom(y - 1, n, p)
    b <- pbinom(y, n, p)
    u <- runif(n = length(y), min = a, max = b)
    qnorm(u)
}
residb1$qr <- qres.binom(b1)

ggplot(residb1, aes(x = .fitted, y = qr)) + geom_point() + geom_smooth() + geom_hline(yintercept = 0, 
    linetype = 2)

probs <- c(0.25, 0.75)
y <- quantile(residb1$qr, probs, names = FALSE, na.rm = TRUE)
x <- qnorm(probs)
slope <- diff(y)/diff(x)
int <- y[1L] - slope * x[1L]
ggplot(residb1, aes(sample = qr)) + geom_qq(size = rel(4)) + geom_abline(intercept = int, 
    slope = slope, linetype = 2, size = 2)

ggplot(residb1, aes(x = .fitted, y = sqrt(abs(qr)))) + geom_point() + geom_smooth() + 
    geom_hline(yintercept = 1)

ggplot(residb1, aes(x = timemin, y = qr)) + geom_point() + geom_smooth() + geom_hline(yintercept = 0, 
    linetype = 2)
ggplot(residb1, aes(x = t.amb, y = qr)) + geom_point() + geom_smooth() + geom_hline(yintercept = 0, 
    linetype = 2)
ggplot(residb1, aes(x = rainpassed2, y = qr)) + geom_point() + geom_smooth() + geom_hline(yintercept = 0, 
    linetype = 2)

#ggplot(residb1, aes(x = mlight, y = qr)) + geom_point() + geom_smooth() + geom_hline(yintercept = 0,linetype = 2)

ggplot(residb1, aes(x = phase, y = qr)) + geom_point() + geom_smooth() + geom_hline(yintercept = 0, 
    linetype = 2)

t1<-simulateResiduals(b1)
plot(t1)

## CONCLUSION: the model is robust enough, it is not overdispersed and the residuals look good

```
#### Plotting GLOBAL model predictions
```{r}
# Plotting model predictions
p1<-plot_model(b2, type = "emm", terms=c("timemin"), show.data=T, show.p=T, show.values = T, axis.lim = c(0,1), dot.size=5, dot.alpha=0.2)  +
  labs(x = "Time of day", y = "Predicted probability of chelaes exposed", title = NULL) +
  theme_classic(base_size = 18) + scale_x_continuous(breaks = c(1200,1260,1320, 1380, 1440), labels = c("20:00","21:00","22:00", "23:00", "00:00"))

p1
ggsave("Plots/Presence Absence behaviors/Global_model/PA_chelae_timemin.png",plot = last_plot(),width=8, height=6, units="in" )

p2<-plot_model(b2, type = "emm", terms=c( "t.amb"), show.data=T, show.p=T, show.values = T, axis.lim = c(0,1), dot.size=5, dot.alpha=0.2)  +
  labs(x = "Temperature (°C)", y = "Predicted probability of chelaes exposed", title = NULL) +
  theme_classic(base_size = 18)
p2
ggsave("Plots/Presence Absence behaviors/Global_model/PA_chelae_temp.png",plot = last_plot(),width=8, height=6, units="in" )


p3<-plot_model(b2, type = "emm", terms=c( "rainpassed2"), show.data=T, show.p=T, show.values = T, axis.lim = c(0,1), dot.size=5, dot.alpha=0.2)  +
  labs(x = "Hours since last rain", y = "Predicted probability of chelaes exposed", title = NULL) +
  theme_classic(base_size = 18)
p3
ggsave("Plots/Presence Absence behaviors/Global_model/PA_chelae_rain.png",plot = last_plot(),width=8, height=6, units="in" )


p4<-plot_model(b2, type = "emm", terms=c( "phase"), show.data=F, show.p=T, show.values = T, axis.lim = c(0,1), dot.size=5, dot.alpha=0.2)  +
  labs(x = "Moon phase", y = "Predicted probability of chelaes exposed", title = NULL) +
  theme_classic(base_size = 18)
p4
ggsave("Plots/Presence Absence behaviors/Global_model/PA_chelae_phase.png",plot = last_plot(),width=8, height=6, units="in" )

all<-ggarrange(p1+ rremove("ylab") ,p2+ rremove("ylab") ,p3+ rremove("ylab") ,p4+ rremove("ylab") , ncol=2, nrow=2, labels=c("A", "B", "C", "D"), hjust=0.25)

all

annotate_figure(all, left=textGrob("Predicted probability of chelaes exposed", rot=90, vjust=0.35, gp=gpar(cex = 1.5)))
ggsave("Plots/Presence Absence behaviors/Global_model/PA_chelae_all.png",plot = last_plot(),width=8, height=8, units="in",bg = "white" )

#plot_model(b2, type = "est",  show.data=T, show.p=T, show.values = T, axis.lim = c(0,1))  +
#  theme_classic(base_size = 18)
```

#### Checking which variables contribute to the model
```{r}

# Checking without the random factor
models <- list(bin~1,
              bin~timemin,
              bin~t.amb,
              bin~rainpassed2,
              bin~phase,
              bin~timemin+t.amb,
              bin~timemin+rainpassed2,
              bin~timemin+phase,
              bin~t.amb+rainpassed2,
               bin~t.amb+phase,
              bin~rainpassed2+phase,
               bin~timemin+t.amb+rainpassed2,
               bin~timemin+t.amb+phase,
              bin~t.amb+rainpassed2+phase,
              bin~timemin+t.amb+rainpassed2+phase)
fits <- map(models, glm,family=binomial, data=chela)
aic <- map_dbl(fits,AIC)
aic
which.min(aic)
models[[which.min(aic)]] 
pander(aictab(fits,as.character(models)))

# This shows that model 15 and model 14 have very close AIC values (menos de 2 unidades de diferencia) entonces voy a compararlos con un anova

models[[15]]
models[[14]]

b2<-glm(bin ~ timemin + t.amb + rainpassed2 + phase, data=chela, family=binomial)
summary(b2)

b3<-glm(bin~ t.amb + rainpassed2 + phase, data=chela, family=binomial)
summary(b3)

anova(b2,b3,test="Chisq")

# Conclusion: the variable time is not really contributing to the model, so I could simplify the model by removing it

pander(summary(b3))
```


#### Checking residuals model without time
```{r}
# Second best model, technically the same as the global model minus the time
summary(b3)
glanceb3<-glance(b3)
glanceb3
#Testing over-disperssion of the model
gofb3 <- with(glanceb3,pchisq(deviance,df.residual,lower=FALSE)) #creating the object that would allow to get the p-value
gofb3 #p-value to test overdispersion
#This model is not significantly overdispersed: X2= 163.4613	, df=153, p=0.27

#Plotting each variable
b3test <- augment(b3) #gets a dataframe with each value foe each variable, covariate, the residuals, fitted, std.resid, .hat, cook sd, etc

lin.temp<- ggplot(b3test, aes(x = t.amb, y = .std.resid)) + geom_count() + 
  scale_size_area(max_size=4) + 
  geom_hline(yintercept = 0, linetype = 2) + 
  geom_smooth() + guides(size = FALSE) 
#Creating the other graphs
lin.rainpassed2 <- lin.temp + aes(x = rainpassed2)
lin.phase <- lin.temp + aes(x = phase)
#Putting all graphs together
grid.arrange(lin.temp, lin.rainpassed2, lin.phase)

#Checking residuals in general
check_assumptions(b3)


t3<-simulateResiduals(b3)
plot(t3)


```

#### Plotting model predictions
```{r}
# Plotting model predictions
#plot_model(b1, type = "emm", terms=c("timemin"), show.data=T, show.p=T, show.values = T, axis.lim = c(0,1))  +
#  labs(x = "Time of day (min)", y = "Predicted Probability of Chelaes exposed", title = NULL) +
#  theme_classic(base_size = 18)
#ggsave("Plots/Presence Absence behaviors/PA_chelae_timemin.png",plot = last_plot(),width=8, height=6, units="in" )

P1<-plot_model(b2, type = "emm", terms=c( "t.amb"), show.data=T, show.p=T, show.values = T, axis.lim = c(0,1), dot.size=5, alpha=0.2)  +
  labs(x = "Temperature (°C)", y = "Predicted Probability of Chelaes exposed", title = NULL) +
  theme_classic(base_size = 18)
P1
ggsave("Plots/Presence Absence behaviors/PA_chelae_temp.png",plot = last_plot(),width=8, height=6, units="in" )


P2<-plot_model(b2, type = "emm", terms=c( "rainpassed2"), show.data=T, show.p=T, show.values = T, axis.lim = c(0,1), dot.size=5, alpha=0.2)  +
  labs(x = "Hours since last rain", y = "Predicted Probability of Chelaes exposed", title = NULL) +
  theme_classic(base_size = 18)
P2
ggsave("Plots/Presence Absence behaviors/PA_chelae_rain.png",plot = last_plot(),width=8, height=6, units="in" )


P3<-plot_model(b2, type = "emm", terms=c( "phase"), show.data=F, show.p=T, show.values = T, axis.lim = c(0,1), dot.size=5, alpha=0.2)  +
  labs(x = "Moon phase", y = "Predicted Probability of Chelaes exposed", title = NULL) +
  theme_classic(base_size = 18)
P3
ggsave("Plots/Presence Absence behaviors/PA_chelae_phase.png",plot = last_plot(),width=8, height=6, units="in" )


P4<-ggplot(chela, aes(y=bin, x=timemin))+geom_point(size=5, alpha=0.2)  +
  labs(x = "Time of day", y = "Predicted Probability of Chelaes exposed", title = NULL) +
  theme_classic(base_size = 18) + scale_x_continuous(breaks = c(1200,1260,1320, 1380, 1440), labels = c("20:00","21:00","22:00", "23:00", "00:00"))
P4

all<-ggarrange(P4+rremove("ylab"),P1+ rremove("ylab") ,P2+ rremove("ylab") ,P3+ rremove("ylab"), labels=c("A", "B", "C", "D"), hjust=0.25)

all

annotate_figure(all, left=textGrob("Predicted probability of chelaes exposed", rot=90, vjust=0.35, gp=gpar(cex = 1.5)))
ggsave("Plots/Presence Absence behaviors/PA_chelae_all.png",plot = last_plot(),width=8, height=8, units="in",bg = "white" )

plot_model(b2, type = "est",  show.data=T, show.p=T, show.values = T, axis.lim = c(0,1))  +
  theme_classic(base_size = 18)
```


#### Descriptive plots
```{r}
# Barplots

#Hour
hourbin<-chela %>% group_by(halfhour, bin) %>%
  summarize(count=n())
hourbin
ggplot(hourbin, aes(x=halfhour, y=bin))+geom_point(aes(size=count)) 

p1<-hourbin%>%ggplot(aes(x=halfhour, y=count, fill=as.factor(bin)))+
  geom_bar(stat="identity", position = position_fill(reverse = TRUE)) + 
  scale_fill_manual(values=c("#4393c3", "#053061")) + 
  ylab("Proportion") + xlab("Hour")+
  theme_classic() +guides(fill=guide_legend(title= "Behavior present")) +
  theme_classic(base_size = 18)+ theme(axis.text.x=element_text(angle=90, hjust=1))
p1
ggsave("Plots/Presence Absence behaviors/Barplots/PA_chelae_hour.png",plot = last_plot(),width=8, height=6, units="in" )

#T.amb
tempbin<-chela%>%  group_by(tempb, bin) %>%
  summarize(count=n())
tempbin
ggplot(tempbin, aes(x=tempb, y=bin))+geom_point(aes(size=count), alpha=0.5) 

p2<-tempbin%>%ggplot(aes(x=tempb, y=count, fill=as.factor(bin)))+
  geom_bar(stat="identity", position = position_fill(reverse = TRUE)) + 
  scale_fill_manual(values=c("#4393c3", "#053061")) + 
  ylab("Proportion") + xlab("Temperature")+
  theme_classic() +guides(fill=guide_legend(title= "Behavior present")) +
  theme_classic(base_size = 18)
p2
ggsave("Plots/Presence Absence behaviors/Barplots/PA_chelae_temp.png",plot = last_plot(),width=8, height=6, units="in" )

#Rain
rainbin<-chela %>% 
  group_by(rainb, bin) %>%
  summarize(count=n())
rainbin
ggplot(rainbin, aes(x=rainb, y=bin))+geom_point(aes(size=count), alpha=0.5) 

p3<-rainbin%>%ggplot(aes(x=rainb, y=count, fill=as.factor(bin)))+
  geom_bar(stat="identity", position = position_fill(reverse = TRUE)) + 
  scale_fill_manual(values=c("#4393c3", "#053061")) + 
  ylab("Proportion") + xlab("Hours since last rain")+
  theme_classic() +guides(fill=guide_legend(title= "Behavior present")) +
  theme_classic(base_size = 18) + theme(axis.text.x=element_text(angle=90, hjust=1))
p3
ggsave("Plots/Presence Absence behaviors/Barplots/PA_chelae_rain.png",plot = last_plot(),width=8, height=6, units="in" )

#Phase
phasebin<-chela %>% 
  group_by(phase, bin) %>%
  summarize(count=n())
phasebin
ggplot(phasebin, aes(x=phase, y=bin))+geom_point(aes(size=count), alpha=0.5) 

p4<-phasebin%>%ggplot(aes(x=phase, y=count, fill=as.factor(bin)))+
  geom_bar(stat="identity", position = position_fill(reverse = TRUE)) + 
  scale_fill_manual(values=c("#4393c3", "#053061")) + 
  ylab("Proportion") + xlab("Moon phase")+
  theme_classic() +guides(fill=guide_legend(title= "Behavior present"))+
  theme_classic(base_size = 18)
p4
ggsave("Plots/Presence Absence behaviors/Barplots/PA_chelae_phase.png",plot = last_plot(),width=8, height=6, units="in" )

all<-ggarrange(p1+rremove("ylab"),p2+ rremove("ylab") ,p3+ rremove("ylab") ,p4+ rremove("ylab"), labels=c("A", "B", "C", "D"), hjust=0.25, common.legend = T, legend="bottom", align="hv")

all

annotate_figure(all, left=textGrob("Proportion", rot=90, vjust=0.35, gp=gpar(cex = 1.5)))
ggsave("Plots/Presence Absence behaviors/Barplots/PA_chelae_all_bar.png",plot = last_plot(),width=8, height=8, units="in",bg = "white" )

```

### PEEKING OUT
#### Determining the global model
```{r}
#Getting the dataset for just this behavior
peek<-databin%>%filter(beh=="S")
sum(peek$bin)
nrow(peek)


peek$rainpassed3<-as.numeric(peek$rainpassed2)
summary(peek)

minus<-min(peek$timemin)
minus
peek$timemin2<-(peek$timemin-minus)/60

b1<-glmer(bin~timemin+t.amb+rainpassed2+phase+(1|colony), data=peek, family=binomial)
summary(b1) # This model gives the isSingular warning: the colony random factor has a variance of zero, the odel is not detecting diferences between the colonies, so I can consider removing it and see which model is better

b2<-glm(bin~timemin+t.amb+rainpassed2+phase, data=peek, family=binomial) # same model as before but without the colony
summary(b2)


# Comparing the models with an anova
anova(b1,b2) # the models are identical: it is the same to include or exclude the random factor, so I will go with the simpler model, without the random factor

# Final model
b2<-glm(bin~timemin+t.amb+rainpassed2+phase, data=peek, family=binomial)
summary(b2)


```

#### Checking residuals of global model

```{r}
# Global model without the random factor (best model according to anova)
## Checking for overdispersion
summary(b2)
glanceb2<-glance(b2)
glanceb2
gofb2 <- with(glanceb2,pchisq(deviance,df.residual,lower=FALSE)) #creating the object that would allow to get the p-value
gofb2 #p-value to test overdispersion
#This model is significantly overdispersed: X2= 190.51, df=152, p=0.02

## Plotting residuals for each variable
b2test <- augment(b2) #gets a dataframe with each value foe each variable, covariate, the residuals, fitted, std.resid, .hat, cook sd, etc
lin.time<- ggplot(b2test, aes(x = timemin, y = .std.resid)) + geom_count() + 
  scale_size_area(max_size=4) + 
  geom_hline(yintercept = 0, linetype = 2) + 
  geom_smooth() + guides(size = FALSE) 
#Creating the other graphs
lin.temp <- lin.time + aes(x = t.amb)
lin.rainpassed2 <- lin.time + aes(x = rainpassed2)
lin.phase <- lin.time + aes(x = phase)
#Putting all graphs together
grid.arrange(lin.time, lin.temp, lin.rainpassed2, lin.phase)

## Checking residuals in general
check_assumptions(b2)
t2<-simulateResiduals(b2)
plot(t2) 

## CONCLUSION: the model is not very robust, it is overdispersed and the residuals look so-so


# Model with the random factor

summary(b1)
gofb1 <- pchisq(190.5,151,lower=FALSE) #creating the object that would allow to get the p-value
gofb1 #p-value to test overdispersion
#This model  is significantly overdispersed: X2= 190.5, df=151, p=0.02


# Checking residuals
residb1 <- augment(b1)
qres.binom <- function(glmer.obj) {
    p <- fitted(glmer.obj)
    y <- glmer.obj@resp$y
    if (!is.null(glmer.obj@resp$weights)) 
        n <- glmer.obj@resp$weights else n <- rep(1, length(y))
    y <- n * y
    a <- pbinom(y - 1, n, p)
    b <- pbinom(y, n, p)
    u <- runif(n = length(y), min = a, max = b)
    qnorm(u)
}
residb1$qr <- qres.binom(b1)

ggplot(residb1, aes(x = .fitted, y = qr)) + geom_point() + geom_smooth() + geom_hline(yintercept = 0, 
    linetype = 2)

probs <- c(0.25, 0.75)
y <- quantile(residb1$qr, probs, names = FALSE, na.rm = TRUE)
x <- qnorm(probs)
slope <- diff(y)/diff(x)
int <- y[1L] - slope * x[1L]
ggplot(residb1, aes(sample = qr)) + geom_qq(size = rel(4)) + geom_abline(intercept = int, 
    slope = slope, linetype = 2, size = 2)

ggplot(residb1, aes(x = .fitted, y = sqrt(abs(qr)))) + geom_point() + geom_smooth() + 
    geom_hline(yintercept = 1)

ggplot(residb1, aes(x = timemin, y = qr)) + geom_point() + geom_smooth() + geom_hline(yintercept = 0, 
    linetype = 2)
ggplot(residb1, aes(x = t.amb, y = qr)) + geom_point() + geom_smooth() + geom_hline(yintercept = 0, 
    linetype = 2)
ggplot(residb1, aes(x = rainpassed2, y = qr)) + geom_point() + geom_smooth() + geom_hline(yintercept = 0, 
    linetype = 2)

ggplot(residb1, aes(x = phase, y = qr)) + geom_point() + geom_smooth() + geom_hline(yintercept = 0, 
    linetype = 2)

t1<-simulateResiduals(b1)
plot(t1)


## CONCLUSION: the model is  is overdispersed and but the residuals look better than the other one


```
#### Plotting GLOBAL model predictions
```{r}
# Plotting model predictions
summary(b2)

p1<-plot_model(b2, type = "emm", terms=c("timemin"), show.data=T, show.p=T, show.values = T, axis.lim = c(0,1), dot.size=5, dot.alpha=0.2)  +
  labs(x = "Time of day", y = "Predicted probability of peeking out", title = NULL) +
  theme_classic(base_size = 18) + scale_x_continuous(breaks = c(1200,1260,1320, 1380, 1440), labels = c("20:00","21:00","22:00", "23:00", "00:00"))

p1
ggsave("Plots/Presence Absence behaviors/Global_model/PA_peek_timemin.png",plot = last_plot(),width=8, height=6, units="in" )

p2<-plot_model(b2, type = "emm", terms=c( "t.amb"), show.data=T, show.p=T, show.values = T, axis.lim = c(0,1), dot.size=5, dot.alpha=0.2)  +
  labs(x = "Temperature (°C)", y = "Predicted probability of peeking out", title = NULL) +
  theme_classic(base_size = 18)
p2
ggsave("Plots/Presence Absence behaviors/Global_model/PA_peek_temp.png",plot = last_plot(),width=8, height=6, units="in" )


p3<-plot_model(b2, type = "emm", terms=c( "rainpassed2"), show.data=T, show.p=T, show.values = T, axis.lim = c(0,1), dot.size=5, dot.alpha=0.2)  +
  labs(x = "Hours since last rain", y = "Predicted probability of peeking out", title = NULL) +
  theme_classic(base_size = 18)
ggsave("Plots/Presence Absence behaviors/Global_model/PA_peek_rain.png",plot = last_plot(),width=8, height=6, units="in" )


p4<-plot_model(b2, type = "emm", terms=c( "phase"), show.data=F, show.p=T, show.values = T, axis.lim = c(0,1), dot.size=5, dot.alpha=0.2)  +
  labs(x = "Moon phase", y = "Predicted probability of peeking out", title = NULL) +
  theme_classic(base_size = 18) 
p4
ggsave("Plots/Presence Absence behaviors/Global_model/PA_peek_phase.png",plot = last_plot(),width=8, height=6, units="in" )

all<-ggarrange(p1+ rremove("ylab") ,p2+ rremove("ylab") ,p3+ rremove("ylab") ,p4+ rremove("ylab") , ncol=2, nrow=2, labels=c("A", "B", "C", "D"), hjust=0.25)

all

annotate_figure(all, left=textGrob("Predicted probability of peeking out", rot=90, vjust=0.35, gp=gpar(cex = 1.5)))
ggsave("Plots/Presence Absence behaviors/Global_model/PA_peek_all.png",plot = last_plot(),width=8, height=8, units="in",bg = "white" )
  
#plot_model(b2, type = "est",  show.data=T, show.p=T, show.values = T, axis.lim = c(0,1))  +
#  theme_classic(base_size = 18)
```

```{r}
# checking which variables contribute more to the model with the random factor
models <- list(bin~1+(1|colony),
              bin~timemin+(1|colony),
              bin~t.amb+(1|colony),
              bin~rainpassed2+(1|colony),
              bin~phase+(1|colony),
              bin~timemin+t.amb+(1|colony),
              bin~timemin+rainpassed2+(1|colony),
              bin~timemin+phase+(1|colony),
              bin~t.amb+rainpassed2+(1|colony),
               bin~t.amb+phase+(1|colony),
              bin~rainpassed2+phase+(1|colony),
               bin~timemin+t.amb+rainpassed2+(1|colony),
               bin~timemin+t.amb+phase+(1|colony),
              bin~t.amb+rainpassed2+phase+(1|colony),
              bin~timemin+t.amb+rainpassed2+phase+(1|colony))


fits <- map(models, glmer,family=binomial, data=peek)
aic <- map_dbl(fits,AIC)
aic
which.min(aic)
models[[which.min(aic)]] 
pander(aictab(fits,as.character(models)))


# This shows that model 15 and model 14 have very close AIC values (menos de 2 unidades de diferencia) entonces voy a compararlos con un anova

models[[15]]
models[[14]]

b2<-glmer(bin ~ timemin + t.amb + rainpassed2 + phase+ (1 | colony), data=peek, family=binomial)
summary(b2)

b3<-glmer(bin ~  t.amb + rainpassed2 + phase+ (1 | colony), data=peek, family=binomial)
summary(b3)

anova(b2,b3,test="Chisq")

# Conclusion: the variable time is not really contributing to the model, so I could simplify the model by removing it


```

#### Checking which variables contribute to the model without the random factor FINAL MODEL
```{r}

# Checking without the random factor
models <- list(bin~1,
              bin~timemin,
              bin~t.amb,
              bin~rainpassed2,
              bin~phase,
              bin~timemin+t.amb,
              bin~timemin+rainpassed2,
              bin~timemin+phase,
              bin~t.amb+rainpassed2,
               bin~t.amb+phase,
              bin~rainpassed2+phase,
               bin~timemin+t.amb+rainpassed2,
               bin~timemin+t.amb+phase,
              bin~t.amb+rainpassed2+phase,
              bin~timemin+t.amb+rainpassed2+phase)
fits <- map(models, glm,family=binomial, data=peek)
aic <- map_dbl(fits,AIC)
aic
which.min(aic)
models[[which.min(aic)]] 
pander(aictab(fits,as.character(models)))

# This shows that model 15 and model 14 have very close AIC values (menos de 2 unidades de diferencia) entonces voy a compararlos con un anova

models[[15]]
models[[14]]

b2<-glm(bin ~ timemin + t.amb + rainpassed2 + phase, data=peek, family=binomial)
summary(b2)

b3<-glm(bin~ t.amb + rainpassed2 + phase, data=peek, family=binomial)
summary(b3)

anova(b2,b3,test="Chisq")

# Conclusion: the variable time is not really contributing to the model, so I could simplify the model by removing it

pander(summary(b3))
```

#### Checking residuals model without time
```{r}
# Second best model, technically the same as the global model minus the time and witout random factor
b3<-glm(bin~ t.amb + rainpassed2 + phase, data=peek, family=binomial)
summary(b3)
summary(b3)
glanceb3<-glance(b3)
glanceb3
#Testing over-disperssion of the model
gofb3 <- with(glanceb3,pchisq(deviance,df.residual,lower=FALSE)) #creating the object that would allow to get the p-value
gofb3 #p-value to test overdispersion
#This model is still significantly overdispersed: X2= 1193.19	, df=153, p=0.015


#Plotting each variable
b3test <- augment(b3) #gets a dataframe with each value foe each variable, covariate, the residuals, fitted, std.resid, .hat, cook sd, etc

lin.temp<- ggplot(b3test, aes(x = t.amb, y = .std.resid)) + geom_count() + 
  scale_size_area(max_size=4) + 
  geom_hline(yintercept = 0, linetype = 2) + 
  geom_smooth() + guides(size = FALSE) 
#Creating the other graphs
lin.rainpassed2 <- lin.temp + aes(x = rainpassed2)
lin.phase <- lin.temp + aes(x = phase)
#Putting all graphs together
grid.arrange(lin.temp, lin.rainpassed2, lin.phase)

#Checking residuals in general
check_assumptions(b3)

t3<-simulateResiduals(b3)
plot(t3)

# conclussion: the model without the random effects and time (the simplest one) is overdispersed as all the other models, however, the residuals look good



# Second best model, technically the same as the global model minus the time and WITH random factor

b3<-glmer(bin ~  t.amb + rainpassed2 + phase+ (1 | colony), data=peek, family=binomial)
summary(b3)
gofb1 <- pchisq(193.2,152,lower=FALSE) #creating the object that would allow to get the p-value
gofb1 #p-value to test overdispersion
#This model  is significantly overdispersed: X2= 193.2, df=152, p=0.013


# Checking residuals
residb1 <- augment(b3)
qres.binom <- function(glmer.obj) {
    p <- fitted(glmer.obj)
    y <- glmer.obj@resp$y
    if (!is.null(glmer.obj@resp$weights)) 
        n <- glmer.obj@resp$weights else n <- rep(1, length(y))
    y <- n * y
    a <- pbinom(y - 1, n, p)
    b <- pbinom(y, n, p)
    u <- runif(n = length(y), min = a, max = b)
    qnorm(u)
}
residb1$qr <- qres.binom(b1)

ggplot(residb1, aes(x = .fitted, y = qr)) + geom_point() + geom_smooth() + geom_hline(yintercept = 0, 
    linetype = 2)

probs <- c(0.25, 0.75)
y <- quantile(residb1$qr, probs, names = FALSE, na.rm = TRUE)
x <- qnorm(probs)
slope <- diff(y)/diff(x)
int <- y[1L] - slope * x[1L]
ggplot(residb1, aes(sample = qr)) + geom_qq(size = rel(4)) + geom_abline(intercept = int, 
    slope = slope, linetype = 2, size = 2)

ggplot(residb1, aes(x = .fitted, y = sqrt(abs(qr)))) + geom_point() + geom_smooth() + 
    geom_hline(yintercept = 1)

ggplot(residb1, aes(x = t.amb, y = qr)) + geom_point() + geom_smooth() + geom_hline(yintercept = 0, 
    linetype = 2)
ggplot(residb1, aes(x = rainpassed2, y = qr)) + geom_point() + geom_smooth() + geom_hline(yintercept = 0, 
    linetype = 2)

ggplot(residb1, aes(x = phase, y = qr)) + geom_point() + geom_smooth() + geom_hline(yintercept = 0, 
    linetype = 2)



t3<-simulateResiduals(b3)
plot(t3)



```
 


#### Plotting model predictions

```{r}
# Plotting model predictions
b1<-glm(bin~ t.amb + rainpassed2 + phase, data=peek, family=binomial)
summary(b1)

P1<-plot_model(b1, type = "emm", terms=c( "t.amb"), show.data=T, show.p=T, show.values = T, axis.lim = c(0,1), dot.size=5, dot.alpha=0.2)  +
  labs(x = "Temperature (°C)", y = "Predicted Probability of peeking out", title = NULL) +
  theme_classic(base_size = 18)
P1
ggsave("Plots/Presence Absence behaviors/PA_peek_temp.png",plot = last_plot(),width=8, height=6, units="in" )

P2<-plot_model(b1, type = "emm", terms=c( "rainpassed2"), show.data=T, show.p=T, show.values = T, axis.lim = c(0,1),dot.size=5, dot.alpha=0.2)  +
  labs(x = "Hours since last rain", y = "Predicted Probability of peeking out", title = NULL) +
  theme_classic(base_size = 18)

P2
ggsave("Plots/Presence Absence behaviors/PA_peek_rain.png",plot = last_plot(),width=8, height=6, units="in" )



P3<-plot_model(b1, type = "emm", terms=c( "phase"), show.data=F, show.p=T, show.values = T, axis.lim = c(0,1),dot.size=5, dot.alpha=0.2)  +
  labs(x = "Moon phase", y = "Predicted Probability of peeking out", title = NULL) +
  theme_classic(base_size = 18)
P3
ggsave("Plots/Presence Absence behaviors/PA_peek_phase.png",plot = last_plot(),width=8, height=6, units="in" )

P4<-ggplot(peek, aes(y=bin, x=timemin))+geom_point(size=5, alpha=0.2)  +
  labs(x = "Time of day", y = "Predicted Probability of peeking out", title = NULL) +
  theme_classic(base_size = 18) + scale_x_continuous(breaks = c(1200,1260,1320, 1380, 1440), labels = c("20:00","21:00","22:00", "23:00", "00:00"))

P4


all<-ggarrange(P4+rremove("ylab"),P1+ rremove("ylab") ,P2+ rremove("ylab") ,P3+ rremove("ylab"), labels=c("A", "B", "C", "D"), hjust=0.25)

all

annotate_figure(all, left=textGrob("Predicted probability of peeking out", rot=90, vjust=0.35, gp=gpar(cex = 1.5)))
ggsave("Plots/Presence Absence behaviors/PA_peek_all.png",plot = last_plot(),width=8, height=8, units="in",bg = "white" )

```
#### Descriptive plots
```{r}
# Barplots

#Hour
hourbin<-peek %>% group_by(halfhour, bin) %>%
  summarize(count=n())
hourbin
ggplot(hourbin, aes(x=halfhour, y=bin))+geom_point(aes(size=count)) 

p1<-hourbin%>%ggplot(aes(x=halfhour, y=count, fill=as.factor(bin)))+
  geom_bar(stat="identity", position = position_fill(reverse = TRUE)) + 
  scale_fill_manual(values=c("#4393c3", "#053061")) + 
  ylab("Proportion") + xlab("Hour")+
  theme_classic() +guides(fill=guide_legend(title= "Behavior present")) +
  theme_classic(base_size = 18)+ theme(axis.text.x=element_text(angle=90, hjust=1))
p1
ggsave("Plots/Presence Absence behaviors/Barplots/PA_peek_hour.png",plot = last_plot(),width=8, height=6, units="in" )

#T.amb
tempbin<-peek%>%  group_by(tempb, bin) %>%
  summarize(count=n())
tempbin
ggplot(tempbin, aes(x=tempb, y=bin))+geom_point(aes(size=count), alpha=0.5) 

p2<-tempbin%>%ggplot(aes(x=tempb, y=count, fill=as.factor(bin)))+
  geom_bar(stat="identity", position = position_fill(reverse = TRUE)) + 
  scale_fill_manual(values=c("#4393c3", "#053061")) + 
  ylab("Proportion") + xlab("Temperature")+
  theme_classic() +guides(fill=guide_legend(title= "Behavior present")) +
  theme_classic(base_size = 18)
p2
ggsave("Plots/Presence Absence behaviors/Barplots/PA_peek_temp.png",plot = last_plot(),width=8, height=6, units="in" )

#Rain
rainbin<-peek %>% 
  group_by(rainb, bin) %>%
  summarize(count=n())
rainbin
ggplot(rainbin, aes(x=rainb, y=bin))+geom_point(aes(size=count), alpha=0.5) 

p3<-rainbin%>%ggplot(aes(x=rainb, y=count, fill=as.factor(bin)))+
  geom_bar(stat="identity", position = position_fill(reverse = TRUE)) + 
  scale_fill_manual(values=c("#4393c3", "#053061")) + 
  ylab("Proportion") + xlab("Hours since last rain")+
  theme_classic() +guides(fill=guide_legend(title= "Behavior present")) +
  theme_classic(base_size = 18) + theme(axis.text.x=element_text(angle=90, hjust=1))
p3
ggsave("Plots/Presence Absence behaviors/Barplots/PA_peek_rain.png",plot = last_plot(),width=8, height=6, units="in" )

#Phase
phasebin<-peek %>% 
  group_by(phase, bin) %>%
  summarize(count=n())
phasebin
ggplot(phasebin, aes(x=phase, y=bin))+geom_point(aes(size=count), alpha=0.5) 

p4<-phasebin%>%ggplot(aes(x=phase, y=count, fill=as.factor(bin)))+
  geom_bar(stat="identity", position = position_fill(reverse = TRUE)) + 
  scale_fill_manual(values=c("#4393c3", "#053061")) + 
  ylab("Proportion") + xlab("Moon phase")+
  theme_classic() +guides(fill=guide_legend(title= "Behavior present"))+
  theme_classic(base_size = 18)
p4
ggsave("Plots/Presence Absence behaviors/Barplots/PA_peek_phase.png",plot = last_plot(),width=8, height=6, units="in" )

all<-ggarrange(p1+rremove("ylab"),p2+ rremove("ylab") ,p3+ rremove("ylab") ,p4+ rremove("ylab"), labels=c("A", "B", "C", "D"), hjust=0.25, common.legend = T, legend="bottom", align="hv")

all

annotate_figure(all, left=textGrob("Proportion", rot=90, vjust=0.35, gp=gpar(cex = 1.5)))
ggsave("Plots/Presence Absence behaviors/Barplots/PA_peek_all_bar.png",plot = last_plot(),width=8, height=8, units="in",bg = "white" )

```

### FEEDING
#### Determining the global model

```{r}
# Getting the dataset for just this behavior
feed<-databin%>%filter(beh=="A")
sum(feed$bin)
nrow(feed)

b1<-glmer(bin~timemin+t.amb+rainpassed2+phase+(1|colony), data=feed, family=binomial)
summary(b1) # This model issues a warning about re-scaling the variables


#feed$rainpassed3<-as.numeric(feed$rainpassed2)
#summary(feed)

minus<-min(feed$timemin)
minus
feed$timemin2<-(feed$timemin-minus)/60 # standarizing it to that the earliest observation is zero and it goes from there, and also converting it to hours

b1<-glmer(bin~timemin2+t.amb+rainpassed2+phase+(1|colony), data=feed, family=binomial)
summary(b1)  # Scaling time gets rid of the convergence issue. It also doesnt have the isSingular issue, so I can keep the random factor
```


#### Checking residuals of global model
```{r}
summary(b1)
gofb1 <- pchisq(167.2,151,lower=FALSE) #creating the object that would allow to get the p-value
gofb1 #p-value to test overdispersion
#This model is not significantly overdispersed: X2= 167.2, df=151, p=0.17

# Checking residuals
#check_assumptions(b1)
residb1 <- augment(b1)
qres.binom <- function(glmer.obj) {
    p <- fitted(glmer.obj)
    y <- glmer.obj@resp$y
    if (!is.null(glmer.obj@resp$weights)) 
        n <- glmer.obj@resp$weights else n <- rep(1, length(y))
    y <- n * y
    a <- pbinom(y - 1, n, p)
    b <- pbinom(y, n, p)
    u <- runif(n = length(y), min = a, max = b)
    qnorm(u)
}
residb1$qr <- qres.binom(b1)

ggplot(residb1, aes(x = .fitted, y = qr)) + geom_point() + geom_smooth() + geom_hline(yintercept = 0, 
    linetype = 2)

probs <- c(0.25, 0.75)
y <- quantile(residb1$qr, probs, names = FALSE, na.rm = TRUE)
x <- qnorm(probs)
slope <- diff(y)/diff(x)
int <- y[1L] - slope * x[1L]
ggplot(residb1, aes(sample = qr)) + geom_qq(size = rel(4)) + geom_abline(intercept = int, 
    slope = slope, linetype = 2, size = 2)

ggplot(residb1, aes(x = .fitted, y = sqrt(abs(qr)))) + geom_point() + geom_smooth() + 
    geom_hline(yintercept = 1)

ggplot(residb1, aes(x = timemin2, y = qr)) + geom_point() + geom_smooth() + geom_hline(yintercept = 0, 
    linetype = 2)
ggplot(residb1, aes(x = t.amb, y = qr)) + geom_point() + geom_smooth() + geom_hline(yintercept = 0, 
    linetype = 2)
ggplot(residb1, aes(x = rainpassed2, y = qr)) + geom_point() + geom_smooth() + geom_hline(yintercept = 0, 
    linetype = 2)

ggplot(residb1, aes(x = phase, y = qr)) + geom_point() + geom_smooth() + geom_hline(yintercept = 0, 
    linetype = 2)

t1<-simulateResiduals(b1)
plot(t1)

## CONCLUSION: the model  is not overdispersed but the residuals dont look good
```

#### Plotting GLOBAL model predictions
```{r}
# Plotting model predictions
summary(b1)

p1<-plot_model(b1, type = "emm", terms=c("timemin2"), show.data=T, show.p=T, show.values = T, axis.lim = c(0,1), dot.size=5, dot.alpha=0.2)  +
  labs(x = "Time of day", y = "Predicted probability of feeding", title = NULL) +
  theme_classic(base_size = 18) + scale_x_continuous(breaks = c(1200,1260,1320, 1380, 1440), labels = c("20:00","21:00","22:00", "23:00", "00:00"))

p1
ggsave("Plots/Presence Absence behaviors/Global_model/PA_feed_timemin.png",plot = last_plot(),width=8, height=6, units="in" )

p2<-plot_model(b1, type = "emm", terms=c( "t.amb"), show.data=T, show.p=T, show.values = T, axis.lim = c(0,1), dot.size=5, dot.alpha=0.2)  +
  labs(x = "Temperature (°C)", y = "Predicted probability of feeding", title = NULL) +
  theme_classic(base_size = 18)
p2
ggsave("Plots/Presence Absence behaviors/Global_model/PA_feed_temp.png",plot = last_plot(),width=8, height=6, units="in" )


p3<-plot_model(b1, type = "emm", terms=c( "rainpassed2"), show.data=T, show.p=T, show.values = T, axis.lim = c(0,1), dot.size=5, dot.alpha=0.2)  +
  labs(x = "Hours since last rain", y = "Predicted probability of feeding", title = NULL) +
  theme_classic(base_size = 18)
p3
ggsave("Plots/Presence Absence behaviors/Global_model/PA_feed_rain.png",plot = last_plot(),width=8, height=6, units="in" )


p4<-plot_model(b1, type = "emm", terms=c( "phase"), show.data=F, show.p=T, show.values = T, axis.lim = c(0,1), dot.size=5, dot.alpha=0.2)  +
  labs(x = "Moon phase", y = "Predicted probability of feeding", title = NULL) +
  theme_classic(base_size = 18) 
p4
ggsave("Plots/Presence Absence behaviors/Global_model/PA_feed_phase.png",plot = last_plot(),width=8, height=6, units="in" )

all<-ggarrange(p1+ rremove("ylab") ,p2+ rremove("ylab") ,p3+ rremove("ylab") ,p4+ rremove("ylab") , ncol=2, nrow=2, labels=c("A", "B", "C", "D"), hjust=0.25)

all

annotate_figure(all, left=textGrob("Predicted probability of feeding", rot=90, vjust=0.35, gp=gpar(cex = 1.5)))
ggsave("Plots/Presence Absence behaviors/Global_model/PA_feed_all.png",plot = last_plot(),width=8, height=8, units="in",bg = "white" )
  
#plot_model(b2, type = "est",  show.data=T, show.p=T, show.values = T, axis.lim = c(0,1))  +
#  theme_classic(base_size = 18)
```
#### Checking which variables contribute more to the model

```{r}
# checking which variables contribute more to the model
models <- list(bin~1+(1|colony),
              bin~timemin2+(1|colony),
              bin~t.amb+(1|colony),
              bin~rainpassed2+(1|colony),
              bin~phase+(1|colony),
              bin~timemin2+t.amb+(1|colony),
              bin~timemin2+rainpassed2+(1|colony),
              bin~timemin2+phase+(1|colony),
              bin~t.amb+rainpassed2+(1|colony),
               bin~t.amb+phase+(1|colony),
              bin~rainpassed2+phase+(1|colony),
               bin~timemin2+t.amb+rainpassed2+(1|colony),
               bin~timemin2+t.amb+phase+(1|colony),
              bin~t.amb+rainpassed2+phase+(1|colony),
              bin~timemin2+t.amb+rainpassed2+phase+(1|colony))

fits <- map(models, glmer,family=binomial, data=feed)
aic <- map_dbl(fits,AIC)
aic
which.min(aic)
models[[which.min(aic)]] 
pander(aictab(fits,as.character(models)))


# Model with the variables that most contribute to the model is the model with no variables... it might be better to just do a description for this behavior of the conditions associated with the presence and the absence
```


The best model is the one with no variables.... o sea, las variables no contrinuyen realmente a expicar la varianza de ver o no un pseudo alimentandose # Model with the variables that most contribute to the model is the model with no variables... it might be better to just do a description for this behavior of the conditions associated with the presence and the absence


Statistical tests: show that the best model to explain the variance of finding a pseudoscorpion feeding is the model with no variables. I will only do a descriptive plot then to show what the conditions were for the presence and absence of Feeding but that those conditions were not really explaining the chance of them feeding

```{r}
b1<-glmer(bin~1+(1|colony), data=feed, family=binomial)
summary(b1)  # Scaling time gets rid of the convergence issue. It also doesnt have the isSingular issue, so I can keep the random factor

b2<-glm(bin~1, data=feed, family="binomial")
summary(b2)

anova(b1,b2)

# It is important to keep the colony identity

summary(b1)
t1<-simulateResiduals(b1)
plot(t1)
```



#### Descriptive plots


```{r}
# Point plots
P1<-ggplot(feed, aes(y=bin, x=t.amb))+geom_point(size=5, alpha=0.2)  +
  labs(x = "Temperature (°C)", y = "Probability of feeding", title = NULL) +
  theme_classic(base_size = 18)
P1

P2<-ggplot(feed, aes(y=bin, x=rainpassed2))+geom_point(size=5, alpha=0.2)  +
  labs(x = "Hours since last rain", y = "Probability of feeding", title = NULL) +
  theme_classic(base_size = 18)
P2

P3<-ggplot(feed, aes(y=bin, x=phase))+geom_count()  + scale_size_area(max_size = 8)+
  labs(x = "Moon phase", y = "Probability of feeding", title = NULL) +
  theme_classic(base_size = 18)

P3

P4<-ggplot(feed, aes(y=bin, x=timemin))+geom_point(size=5, alpha=0.2)  +
  labs(x = "Time of day", y = "Probability of feeding", title = NULL) +
  theme_classic(base_size = 18)+ scale_x_continuous(breaks = c(1200,1260,1320, 1380, 1440), labels = c("20:00","21:00","22:00", "23:00", "00:00"))

P4

all<-ggarrange(P4+rremove("ylab"),P1+ rremove("ylab") ,P2+ rremove("ylab") ,P3+ rremove("ylab"), labels=c("A", "B", "C", "D"), hjust=0.25)

all

annotate_figure(all, left=textGrob("Probability of feeding", rot=90, vjust=0.35, gp=gpar(cex = 1.5)))
ggsave("Plots/Presence Absence behaviors/PA_feed_all.png",plot = last_plot(),width=8, height=8, units="in",bg = "white" )
```

```{r}
# Barplots

#Hour
hourbin<-feed %>% group_by(halfhour, bin) %>%
  summarize(count=n())
hourbin
ggplot(hourbin, aes(x=halfhour, y=bin))+geom_point(aes(size=count)) 

p1<-hourbin%>%ggplot(aes(x=halfhour, y=count, fill=as.factor(bin)))+
  geom_bar(stat="identity", position = position_fill(reverse = TRUE)) + 
  scale_fill_manual(values=c("#4393c3", "#053061")) + 
  ylab("Proportion") + xlab("Hour")+
  theme_classic() +guides(fill=guide_legend(title= "Behavior present")) +
  theme_classic(base_size = 18)+ theme(axis.text.x=element_text(angle=90, hjust=1))
p1
ggsave("Plots/Presence Absence behaviors/Barplots/PA_feed_hour.png",plot = last_plot(),width=8, height=6, units="in" )


#T.amb
tempbin<-feed%>%  group_by(tempb, bin) %>%
  summarize(count=n())
tempbin
ggplot(tempbin, aes(x=tempb, y=bin))+geom_point(aes(size=count), alpha=0.5) 

p2<-tempbin%>%ggplot(aes(x=tempb, y=count, fill=as.factor(bin)))+
  geom_bar(stat="identity", position = position_fill(reverse = TRUE)) + 
  scale_fill_manual(values=c("#4393c3", "#053061")) + 
  ylab("Proportion") + xlab("Temperature")+
  theme_classic() +guides(fill=guide_legend(title= "Behavior present")) +
  theme_classic(base_size = 18)
p2
ggsave("Plots/Presence Absence behaviors/Barplots/PA_feed_temp.png",plot = last_plot(),width=8, height=6, units="in" )

#Rain
rainbin<-feed %>% 
  group_by(rainb, bin) %>%
  summarize(count=n())
rainbin
ggplot(rainbin, aes(x=rainb, y=bin))+geom_point(aes(size=count), alpha=0.5) 

p3<-rainbin%>%ggplot(aes(x=rainb, y=count, fill=as.factor(bin)))+
  geom_bar(stat="identity", position = position_fill(reverse = TRUE)) + 
  scale_fill_manual(values=c("#4393c3", "#053061")) + 
  ylab("Proportion") + xlab("Hours since last rain")+
  theme_classic() +guides(fill=guide_legend(title= "Behavior present")) +
  theme_classic(base_size = 18) + theme(axis.text.x=element_text(angle=90, hjust=1))
p3

ggsave("Plots/Presence Absence behaviors/Barplots/PA_feed_rain.png",plot = last_plot(),width=8, height=6, units="in" )

#Phase
phasebin<-feed %>% 
  group_by(phase, bin) %>%
  summarize(count=n())
phasebin
ggplot(phasebin, aes(x=phase, y=bin))+geom_point(aes(size=count), alpha=0.5) 

p4<-phasebin%>%ggplot(aes(x=phase, y=count, fill=as.factor(bin)))+
  geom_bar(stat="identity", position = position_fill(reverse = TRUE)) + 
  scale_fill_manual(values=c("#4393c3", "#053061")) + 
  ylab("Proportion") + xlab("Moon phase")+
  theme_classic() +guides(fill=guide_legend(title= "Behavior present"))+
  theme_classic(base_size = 18)
p4

ggsave("Plots/Presence Absence behaviors/Barplots/PA_feed_phase.png",plot = last_plot(),width=8, height=6, units="in" )

all<-ggarrange(p1+rremove("ylab"),p2+ rremove("ylab") ,p3+ rremove("ylab") ,p4+ rremove("ylab"), labels=c("A", "B", "C", "D"), hjust=0.25, common.legend = T, legend="bottom", align="hv")

all

annotate_figure(all, left=textGrob("Proportion", rot=90, vjust=0.35, gp=gpar(cex = 1.5)))
ggsave("Plots/Presence Absence behaviors/Barplots/PA_feed_all_bar.png",plot = last_plot(),width=8, height=8, units="in",bg = "white" )

#Colony
colbin<-feed %>% 
  group_by(colony, bin) %>%
  summarize(count=n())
colbin
ggplot(colbin, aes(x=colony, y=bin))+geom_point(aes(size=count), alpha=0.5) 

p5<-colbin%>%ggplot(aes(x=colony, y=count, fill=as.factor(bin)))+
  geom_bar(stat="identity", position = position_fill(reverse = TRUE)) + 
  scale_fill_manual(values=c("#4393c3", "#053061")) + 
  ylab("Proportion") + xlab("Colony")+
  theme_classic() +guides(fill=guide_legend(title= "Behavior present"))+
  theme_classic(base_size = 18)+theme(legend.position = "top")
p5

ggsave("Plots/Presence Absence behaviors/Barplots/PA_feed_colony.png",plot = last_plot(),width=8, height=6, units="in" )



```



### OUTSIDE 2: 

Since there were only 61 instance of walking and 11 of outside, we decided to merge the dataset as just outside the crevice
```{r}
out<-databin %>% filter(beh2=="Outside")
sum(out$bin)
nrow(out)


b1<-glmer(bin~timemin+t.amb+rainpassed2+phase+(1|colony), data=out, family=binomial)
summary(b1) #IT gives me a error about scaling the variables

out$rainpassed3<-as.numeric(out$rainpassed2)
summary(out)

minus<-min(out$timemin)
minus
out$timemin2<-(out$timemin-minus)/60

b1<-glmer(bin~timemin2+t.amb+rainpassed3+phase+(1|colony), data=out, family=binomial)
summary(b1)

b2<-glm(bin~timemin2+t.amb+rainpassed3+phase, data=out, family=binomial)
summary(b2)

anova(b1,b2) # There is no difference on the models, so I will use the one without the random factor
```

#### Checking residuals of global model

```{r}
## Checking for overdispersion
summary(b2)
glanceb2<-glance(b2)
glanceb2
gofb2 <- with(glanceb2,pchisq(deviance,df.residual,lower=FALSE)) #creating the object that would allow to get the p-value
gofb2 #p-value to test overdispersion
#This model is not significantly overdispersed: X2= 327.3, df=311, p=0.25

## Plotting residuals for each variable
b2test <- augment(b2) #gets a dataframe with each value foe each variable, covariate, the residuals, fitted, std.resid, .hat, cook sd, etc
lin.time<- ggplot(b2test, aes(x = timemin2, y = .std.resid)) + geom_count() + 
  scale_size_area(max_size=4) + 
  geom_hline(yintercept = 0, linetype = 2) + 
  geom_smooth() + guides(size = FALSE) 
#Creating the other graphs
lin.temp <- lin.time + aes(x = t.amb)
lin.rainpassed2 <- lin.time + aes(x = rainpassed3)
lin.phase <- lin.time + aes(x = phase)
#Putting all graphs together
grid.arrange(lin.time, lin.temp, lin.rainpassed2, lin.phase)

## Checking residuals in general
check_assumptions(b2)
t2<-simulateResiduals(b2)
plot(t2) 

## CONCLUSION: the model is robust enough, it is not overdispersed and the residuals look good
```

#### Plotting GLOBAL model predictions
```{r}
# Plotting model predictions
summary(b2)

p1<-plot_model(b2, type = "emm", terms=c("timemin2"), show.data=T, show.p=T, show.values = T, axis.lim = c(0,1), dot.size=5, dot.alpha=0.2)  +
  labs(x = "Time of day", y = "Predicted probability of being outside", title = NULL) +
  theme_classic(base_size = 18)+ scale_x_continuous(breaks = c(-0.23,0.77,1.77, 2.77, 3.77), labels = c("20:00","21:00","22:00", "23:00", "00:00"))

p1
ggsave("Plots/Presence Absence behaviors/Global_model/PA_out_timemin.png",plot = last_plot(),width=8, height=6, units="in" )

p2<-plot_model(b2, type = "emm", terms=c( "t.amb"), show.data=T, show.p=T, show.values = T, axis.lim = c(0,1), dot.size=5, dot.alpha=0.2)  +
  labs(x = "Temperature (°C)", y = "Predicted probability of being outside", title = NULL) +
  theme_classic(base_size = 18)
p2
ggsave("Plots/Presence Absence behaviors/Global_model/PA_out_temp.png",plot = last_plot(),width=8, height=6, units="in" )


p3<-plot_model(b2, type = "emm", terms=c( "rainpassed3"), show.data=T, show.p=T, show.values = T, axis.lim = c(0,1), dot.size=5, dot.alpha=0.2)  +
  labs(x = "Hours since last rain", y = "Predicted probability of being outside", title = NULL) +
  theme_classic(base_size = 18)
p3
ggsave("Plots/Presence Absence behaviors/Global_model/PA_out_rain.png",plot = last_plot(),width=8, height=6, units="in" )


p4<-plot_model(b2, type = "emm", terms=c( "phase"), show.data=F, show.p=T, show.values = T, axis.lim = c(0,1), dot.size=5, dot.alpha=0.2)  +
  labs(x = "Moon phase", y = "Predicted probability of being outside", title = NULL) +
  theme_classic(base_size = 18) 
p4
ggsave("Plots/Presence Absence behaviors/Global_model/PA_out_phase.png",plot = last_plot(),width=8, height=6, units="in" )

all<-ggarrange(p1+ rremove("ylab") ,p2+ rremove("ylab") ,p3+ rremove("ylab") ,p4+ rremove("ylab") , ncol=2, nrow=2, labels=c("A", "B", "C", "D"), hjust=0.25)

all

annotate_figure(all, left=textGrob("Predicted probability of being outside", rot=90, vjust=0.35, gp=gpar(cex = 1.5)))
ggsave("Plots/Presence Absence behaviors/Global_model/PA_out_all.png",plot = last_plot(),width=8, height=8, units="in",bg = "white" )
  
#plot_model(b2, type = "est",  show.data=T, show.p=T, show.values = T, axis.lim = c(0,1))  +
#  theme_classic(base_size = 18)
```



#### Checking which variables contribute more to the model 

```{r}
# Model with the variables that most contribute to the model FINAL MODEL


# Checking without the random effect
models <- list(bin~1,
              bin~timemin2,
              bin~t.amb,
              bin~rainpassed3,
              bin~phase,
              bin~timemin2+t.amb,
              bin~timemin2+rainpassed3,
              bin~timemin2+phase,
              bin~t.amb+rainpassed3,
               bin~t.amb+phase,
              bin~rainpassed3+phase,
               bin~timemin2+t.amb+rainpassed3,
               bin~timemin2+t.amb+phase,
              bin~t.amb+rainpassed3+phase,
              bin~timemin2+t.amb+rainpassed3+phase)


fits <- map(models, glm,family=binomial, data=out)
aic <- map_dbl(fits,AIC)
aic
which.min(aic)
models[[which.min(aic)]] 
pander(aictab(fits,as.character(models)))



# Model with the variables that most contribute to the model
b2<-glm(bin~ rainpassed3 , data=out, family=binomial)
summary(b2)

#which(!models$converged) # Models that had convergence issues

#pander(model.sel(models$fits))


summary(models$fit[[4]]) 
```



```{r}
# checking which variables contribute more to the model to test for the random factor
models <- list(bin~1+(1|colony),
              bin~timemin2+(1|colony),
              bin~t.amb+(1|colony),
              bin~rainpassed3+(1|colony),
              bin~phase+(1|colony),
              bin~timemin2+t.amb+(1|colony),
              bin~timemin2+rainpassed3+(1|colony),
              bin~timemin2+phase+(1|colony),
              bin~t.amb+rainpassed3+(1|colony),
               bin~t.amb+phase+(1|colony),
              bin~rainpassed3+phase+(1|colony),
               bin~timemin2+t.amb+rainpassed3+(1|colony),
               bin~timemin2+t.amb+phase+(1|colony),
              bin~t.amb+rainpassed3+phase+(1|colony),
              bin~timemin2+t.amb+rainpassed3+phase+(1|colony))


fits <- map(models, glmer,family=binomial, data=out)
aic <- map_dbl(fits,AIC)
aic
which.min(aic)
models[[which.min(aic)]]

b3<-glm(bin~rainpassed3, data=out, family=binomial)
summary(b3)
b4<-glm(bin~t.amb +rainpassed3, data=out, family=binomial)
summary(b4)
b5<-glm(bin~timemin2+t.amb +rainpassed3, data=out, family=binomial)
summary(b5)
b6<-glm(bin~1, data=out, family=binomial)

anova(b2,b3, test="Chisq") #No difference

anova(b3,b4, test="Chisq") #No difference

anova(b3,b5, test="Chisq") #no difference

anova(b2,b6, test="Chisq") # difference

anova(b3,b6, test="Chisq") # difference

# The best model is the one with just the rain and without the random factor

b3<-glm(bin~rainpassed3, data=out, family=binomial)
summary(b3)

```
#### Checking residuals of final model
```{r}

summary(b3)
glanceb3<-glance(b3)
glanceb3
#Testing over-disperssion of the model
gofb3 <- with(glanceb3,pchisq(deviance,df.residual,lower=FALSE)) #creating the object that would allow to get the p-value
gofb3 #p-value to test overdispersion
#This model is not significantly overdispersed: X2= 332.63	, df=316, p=0.27

#Plotting each variable
b3test <- augment(b3) #gets a dataframe with each value foe each variable, covariate, the residuals, fitted, std.resid, .hat, cook sd, etc

lin.temp<- ggplot(b3test, aes(x = t.amb, y = .std.resid)) + geom_count() + 
  scale_size_area(max_size=4) + 
  geom_hline(yintercept = 0, linetype = 2) + 
  geom_smooth() + guides(size = FALSE) 
#Creating the other graphs
lin.rainpassed3 <- lin.temp + aes(x = rainpassed3)
lin.rainpassed3

#Checking residuals in general
check_assumptions(b3)


t3<-simulateResiduals(b3)
plot(t3)


```


#### Plotting model predictions

```{r}
# Plotting model predictions
P3<-plot_model(b3, type = "pred", terms=c( "rainpassed3"), show.data=T, show.p=T, show.values = T, axis.lim = c(0,1),dot.size=5, dot.alpha=0.2)  +
  labs(x = "Hours since last rain", y = "Predicted Probability of being outside", title = NULL) +
  theme_classic(base_size = 18)
P3
ggsave("Plots/Presence Absence behaviors/PA_out_rain.png",plot = last_plot(),width=8, height=6, units="in" )



# Plotting other variables
## Bubble plot
#time
P1<-ggplot(data=out, aes(y=bin, x=timemin2))+geom_point(alpha=0.2, size=5) +
  labs(x = "Time of day (min)", y = "Observations of individuals outside", title = NULL) +
  theme_classic(base_size = 18)+ scale_x_continuous(breaks = c(-0.23,0.77,1.77, 2.77, 3.77), labels = c("20:00","21:00","22:00", "23:00", "00:00"))
P1


# Temperature
P2<-ggplot(data=out, aes(y=bin, x=t.amb))+geom_point(alpha=0.2, size=5) +
  labs(x = "Temperature (°C)", y = "Observations of individuals outside", title = NULL) +
  theme_classic(base_size = 18)
P2

#Phase
P4<-ggplot(data=out, aes(y=bin, x=phase))+geom_count() + scale_size_area(max_size=8) +
  labs(x = "Lunar phase", y = "Observations of individuals outside", title = NULL) +
  theme_classic(base_size = 18) 
P4




all<-ggarrange(P1+rremove("ylab"),P2+ rremove("ylab") ,P3+ rremove("ylab") ,P4+ rremove("ylab"), labels=c("A", "B", "C", "D"), hjust=0.25)

all

annotate_figure(all, left=textGrob("Predicted probability of being outside", rot=90, vjust=0.35, gp=gpar(cex = 1.5)))
ggsave("Plots/Presence Absence behaviors/PA_out_all.png",plot = last_plot(),width=8, height=8, units="in",bg = "white" )

## Barplot
out%>%ggplot(aes(x=phase, fill=as.factor(bin)))+
  geom_bar( position = position_fill(reverse = TRUE)) + 
  scale_fill_manual(values=c("#4393c3", "#053061")) + 
  ylab("Proportion") + xlab("Temperature")+
  theme_classic() +guides(fill=guide_legend(title= "Behavior present")) + 
  facet_wrap(~beh2, ncol=1)

```

#### Descriptive plots
```{r}
# Barplots

#Hour
hourbin<-out %>% group_by(halfhour, bin) %>%
  summarize(count=n())
hourbin
ggplot(hourbin, aes(x=halfhour, y=bin))+geom_point(aes(size=count)) 

p1<-hourbin%>%ggplot(aes(x=halfhour, y=count, fill=as.factor(bin)))+
  geom_bar(stat="identity", position = position_fill(reverse = TRUE)) + 
  scale_fill_manual(values=c("#4393c3", "#053061")) + 
  ylab("Proportion") + xlab("Hour")+
  theme_classic() +guides(fill=guide_legend(title= "Behavior present")) +
  theme_classic(base_size = 18)+ theme(axis.text.x=element_text(angle=90, hjust=1))
p1
ggsave("Plots/Presence Absence behaviors/Barplots/PA_out_hour.png",plot = last_plot(),width=8, height=6, units="in" )

#T.amb
tempbin<-out%>%  group_by(tempb, bin) %>%
  summarize(count=n())
tempbin
ggplot(tempbin, aes(x=tempb, y=bin))+geom_point(aes(size=count), alpha=0.5) 

p2<-tempbin%>%ggplot(aes(x=tempb, y=count, fill=as.factor(bin)))+
  geom_bar(stat="identity", position = position_fill(reverse = TRUE)) + 
  scale_fill_manual(values=c("#4393c3", "#053061")) + 
  ylab("Proportion") + xlab("Temperature")+
  theme_classic() +guides(fill=guide_legend(title= "Behavior present")) +
  theme_classic(base_size = 18)
p2
ggsave("Plots/Presence Absence behaviors/Barplots/PA_out_temp.png",plot = last_plot(),width=8, height=6, units="in" )

#Rain
rainbin<-out %>% 
  group_by(rainb, bin) %>%
  summarize(count=n())
rainbin
ggplot(rainbin, aes(x=rainb, y=bin))+geom_point(aes(size=count), alpha=0.5) 

p3<-rainbin%>%ggplot(aes(x=rainb, y=count, fill=as.factor(bin)))+
  geom_bar(stat="identity", position = position_fill(reverse = TRUE)) + 
  scale_fill_manual(values=c("#4393c3", "#053061")) + 
  ylab("Proportion") + xlab("Hours since last rain")+
  theme_classic() +guides(fill=guide_legend(title= "Behavior present")) +
  theme_classic(base_size = 18) + theme(axis.text.x=element_text(angle=90, hjust=1))
p3
ggsave("Plots/Presence Absence behaviors/Barplots/PA_out_rain.png",plot = last_plot(),width=8, height=6, units="in" )

#Phase
phasebin<-out%>% 
  group_by(phase, bin) %>%
  summarize(count=n())
phasebin
ggplot(phasebin, aes(x=phase, y=bin))+geom_point(aes(size=count), alpha=0.5) 

p4<-phasebin%>%ggplot(aes(x=phase, y=count, fill=as.factor(bin)))+
  geom_bar(stat="identity", position = position_fill(reverse = TRUE)) + 
  scale_fill_manual(values=c("#4393c3", "#053061")) + 
  ylab("Proportion") + xlab("Moon phase")+
  theme_classic() +guides(fill=guide_legend(title= "Behavior present"))+
  theme_classic(base_size = 18)
p4
ggsave("Plots/Presence Absence behaviors/Barplots/PA_out_phase.png",plot = last_plot(),width=8, height=6, units="in" )

all<-ggarrange(p1+rremove("ylab"),p2+ rremove("ylab") ,p3+ rremove("ylab") ,p4+ rremove("ylab"), labels=c("A", "B", "C", "D"), hjust=0.25, common.legend = T, legend="bottom", align="hv")

all

annotate_figure(all, left=textGrob("Proportion", rot=90, vjust=0.35, gp=gpar(cex = 1.5)))
ggsave("Plots/Presence Absence behaviors/Barplots/PA_out_all_bar.png",plot = last_plot(),width=8, height=8, units="in",bg = "white" )

```

 
## Plotting ALL BEHAVIORS data with bubble plots and barplots
```{r}
#Hour
hourbin<-databin %>% filter(beh2!="Hiding") %>% group_by(beh2, halfhour, bin) %>%
  summarize(count=n())
hourbin
ggplot(hourbin, aes(x=halfhour, y=bin))+geom_point(aes(size=count)) + facet_wrap(~beh2, ncol=1)

hourbin%>%ggplot(aes(x=halfhour, y=count, fill=as.factor(bin)))+
  geom_bar(stat="identity", position = position_fill(reverse = TRUE)) + 
  scale_fill_manual(values=c("#4393c3", "#053061")) + 
  ylab("Proportion") + xlab("Hour")+
  guides(fill=guide_legend(title= "Behavior present")) + 
  facet_wrap(~beh2, ncol=2)+
  theme_classic(base_size = 18) +theme(legend.position = "top", axis.text.x=element_text(angle=90, hjust=1))
ggsave("Plots/Presence Absence behaviors/Barplots/PA_allbeh_hour.png",plot = last_plot(),width=8, height=8, units="in",bg = "white" )

#T.amb
tempbin<-databin %>% filter(beh2!="Hiding") %>% group_by(beh2, tempb, bin) %>%
  summarize(count=n())
tempbin
ggplot(tempbin, aes(x=tempb, y=bin))+geom_point(aes(size=count), alpha=0.5) + facet_wrap(~beh2, ncol=2)

tempbin%>%ggplot(aes(x=tempb, y=count, fill=as.factor(bin)))+
  geom_bar(stat="identity", position = position_fill(reverse = TRUE)) + 
  scale_fill_manual(values=c("#4393c3", "#053061")) + 
  ylab("Proportion") + xlab("Temperature")+
  guides(fill=guide_legend(title= "Behavior present")) + 
  facet_wrap(~beh2, ncol=2)+
  theme_classic(base_size = 18) +theme(legend.position = "top")
ggsave("Plots/Presence Absence behaviors/Barplots/PA_allbeh_temp.png",plot = last_plot(),width=8, height=8, units="in",bg = "white" )

#Rain
rainbin<-databin %>% filter(beh2!="Hiding") %>% 
  group_by(beh2, rainb, bin) %>%
  summarize(count=n())
rainbin
ggplot(rainbin, aes(x=rainb, y=bin))+geom_point(aes(size=count), alpha=0.5) + facet_wrap(~beh2, ncol=2)

rainbin%>%ggplot(aes(x=rainb, y=count, fill=as.factor(bin)))+
  geom_bar(stat="identity", position = position_fill(reverse = TRUE)) + 
  scale_fill_manual(values=c("#4393c3", "#053061")) + 
  ylab("Proportion") + xlab("Temperature")+
guides(fill=guide_legend(title= "Behavior present")) + 
  facet_wrap(~beh2, ncol=2)+
  theme_classic(base_size = 18) +theme(legend.position = "top", axis.text.x=element_text(angle=90, hjust=1))
ggsave("Plots/Presence Absence behaviors/Barplots/PA_allbeh_rain.png",plot = last_plot(),width=8, height=8, units="in",bg = "white" )

#Phase
phasebin<-databin %>% filter(beh2!="Hiding") %>%
  group_by(beh2, phase, bin) %>%
  summarize(count=n())
phasebin
ggplot(phasebin, aes(x=phase, y=bin))+geom_point(aes(size=count), alpha=0.5) + facet_wrap(~beh2, ncol=2)

phasebin%>%ggplot(aes(x=phase, y=count, fill=as.factor(bin)))+
  geom_bar(stat="identity", position = position_fill(reverse = TRUE)) + 
  scale_fill_manual(values=c("#4393c3", "#053061")) + 
  ylab("Proportion") + xlab("Temperature")+
  guides(fill=guide_legend(title= "Behavior present")) + 
  facet_wrap(~beh2, ncol=2)+
  theme_classic(base_size = 18) +theme(legend.position = "top")
ggsave("Plots/Presence Absence behaviors/Barplots/PA_allbeh_phase.png",plot = last_plot(),width=8, height=8, units="in",bg = "white" )
```





## PRESENCE/ABSENCE of each behavior: Only BCI colonies between 8pm and 4am

### Organizing the data
```{r}
# Total number of pseudoscorpions doing the activity
databinb<-data3 %>% 
  filter(location=="BCI") %>%
  pivot_longer(cols=(6:11), names_to = "beh" , values_to="inds") %>%
  mutate(prop=inds/total, 
         hour2=factor(hour,levels=c("20","21", "22", "23", "0", "1", "2", "3", "4")),
         bin=if_else(inds>0,1,0),
         beh2=case_when(beh=="A"~"Feeding",
                        beh=="C"~"Outside",
                        beh=="E"~"Hiding",
                        beh=="F"~"Outside",
                        beh=="Q"~"Chelaes exp.",
                        beh=="S"~"Peeking out",
                        TRUE~NA),
         timesec=as.numeric(time),
         timesec2=as.numeric(daytime),
         timesec3=if_else(timesec<43200,timesec+86400,timesec),
         timemin=timesec3/60,
         timemin2=timemin-min(timemin))


databinb<-databinb %>%  dplyr::select(colony, timesec3,timemin,timemin2, daytime, t.amb, rainpassed2, mlight, phase, bin, total, beh, beh2)


summary(databinb)


```


### Chelaes exposed
```{r}
chela<-databinb%>%filter(beh=="Q")
sum(chela$bin)
nrow(chela)

ggplot(chela, aes(x=timemin))+geom_histogram(binwidth=60)+ ylab("# Observations") + xlab("Time ")+theme_classic()+ facet_wrap(~colony)
ggplot(chela, aes(x=timemin))+geom_histogram(binwidth=60)+ ylab("# Observations") + xlab(" Time")+theme_classic()

chela2<-chela %>% filter(bin==1)
ggplot(chela2, aes(x=timemin))+geom_histogram(binwidth=60)+ ylab("# Observations") + xlab("Time ")+theme_classic()+ facet_wrap(~colony)
ggplot(chela2, aes(x=timemin))+geom_histogram(binwidth=60)+ ylab("# Observations") + xlab(" Time")+theme_classic()
```


```{r}
b1<-glmer(bin~timemin+(1|colony), data=chela, family=binomial)
summary(b1)

b1<-glm(bin~timemin+t.amb+rainpassed2+phase, data=chela, family=binomial)
summary(b1)

b1<-glm(bin~timemin, data=chela, family=binomial)
summary(b1)

b1<-glmer(bin~timemin+t.amb+rainpassed2+phase+(1|colony), data=chela, family=binomial)
summary(b1)

# Checking the if the results change if doing it by colony
chelabci5<-databinb%>%filter(beh=="Q") %>% filter(colony=="BCI5")

b1<-glm(bin~timemin+t.amb+rainpassed2+phase, data=chelabci5, family=binomial)
summary(b1)
b1<-glm(bin~timemin, data=chelabci5, family=binomial)
summary(b1)

chelabci6<-databinb%>%filter(beh=="Q") %>% filter(colony=="BCI6")

b1<-glm(bin~timemin+t.amb+rainpassed2+phase, data=chelabci6, family=binomial)
summary(b1)
b1<-glm(bin~timemin, data=chelabci6, family=binomial)
summary(b1)


b1<-glm(bin~timemin+t.amb+rainpassed2+phase, data=chela, family=binomial)
summary(b1)

b1<-glmer(bin~timemin+t.amb+rainpassed2+phase+(1|colony), data=chela, family=binomial)
summary(b1)

# Checking residuals
library(statmod)
library(broom.mixed)
residb1 <- augment(b1)
qres.binom <- function(glmer.obj) {
    p <- fitted(glmer.obj)
    y <- glmer.obj@resp$y
    if (!is.null(glmer.obj@resp$weights)) 
        n <- glmer.obj@resp$weights else n <- rep(1, length(y))
    y <- n * y
    a <- pbinom(y - 1, n, p)
    b <- pbinom(y, n, p)
    u <- runif(n = length(y), min = a, max = b)
    qnorm(u)
}
residb1$qr <- qres.binom(b1)

ggplot(residb1, aes(x = .fitted, y = qr)) + geom_point() + geom_smooth() + geom_hline(yintercept = 0, 
    linetype = 2)

probs <- c(0.25, 0.75)
y <- quantile(residb1$qr, probs, names = FALSE, na.rm = TRUE)
x <- qnorm(probs)
slope <- diff(y)/diff(x)
int <- y[1L] - slope * x[1L]
ggplot(residb1, aes(sample = qr)) + geom_qq(size = rel(4)) + geom_abline(intercept = int, 
    slope = slope, linetype = 2, size = 2)

ggplot(residb1, aes(x = .fitted, y = sqrt(abs(qr)))) + geom_point() + geom_smooth() + 
    geom_hline(yintercept = 1)

ggplot(residb1, aes(x = timemin, y = qr)) + geom_point() + geom_smooth() + geom_hline(yintercept = 0, 
    linetype = 2)
ggplot(residb1, aes(x = t.amb, y = qr)) + geom_point() + geom_smooth() + geom_hline(yintercept = 0, 
    linetype = 2)
ggplot(residb1, aes(x = rainpassed2, y = qr)) + geom_point() + geom_smooth() + geom_hline(yintercept = 0, 
    linetype = 2)

ggplot(residb1, aes(x = phase, y = qr)) + geom_point() + geom_smooth() + geom_hline(yintercept = 0, 
    linetype = 2)

# Plotting model predictions
plot_model(b1, type = "emm", terms=c("timemin"), show.data=T, show.p=T, show.values = T, axis.lim = c(0,1))  +
  labs(x = "Time of day", y = "Predicted Probability of Chelaes exposed", title = NULL) +
  theme_classic(base_size = 18) + scale_x_continuous(breaks = c(1200,1260,1320, 1380, 1440), labels = c("20:00","21:00","22:00", "23:00", "00:00"))

ggsave("Plots/Presence Absence behaviors/PABCI_chelae_timemin.png",plot = last_plot(),width=8, height=6, units="in" )

plot_model(b1, type = "emm", terms=c( "t.amb"), show.data=T, show.p=T, show.values = T, axis.lim = c(0,1))  +
  labs(x = "Temperature (°C)", y = "Predicted Probability of Chelaes exposed", title = NULL) +
  theme_classic(base_size = 18)
ggsave("Plots/Presence Absence behaviors/PABCI_chelae_temp.png",plot = last_plot(),width=8, height=6, units="in" )


plot_model(b1, type = "emm", terms=c( "rainpassed2"), show.data=T, show.p=T, show.values = T, axis.lim = c(0,1))  +
  labs(x = "Hours since last rain", y = "Predicted Probability of Chelaes exposed", title = NULL) +
  theme_classic(base_size = 18)
ggsave("Plots/Presence Absence behaviors/PABCI_chelae_rain.png",plot = last_plot(),width=8, height=6, units="in" )



plot_model(b1, type = "emm", terms=c( "phase"), show.data=T, show.p=T, show.values = T, axis.lim = c(0,1))  +
  labs(x = "Moon phase", y = "Predicted Probability of Chelaes exposed", title = NULL) +
  theme_classic(base_size = 18)
ggsave("Plots/Presence Absence behaviors/PABCI_chelae_phase.png",plot = last_plot(),width=8, height=6, units="in" )

plot_model(b1, type = "est",  show.data=T, show.p=T, show.values = T, axis.lim = c(0,1))  +
  theme_classic(base_size = 18)


# checking which variables contribute more to the model
models <- list(bin~1+(1|colony),
              bin~timemin+(1|colony),
              bin~t.amb+(1|colony),
              bin~rainpassed2+(1|colony),
              bin~phase+(1|colony),
              bin~timemin+t.amb+(1|colony),
              bin~timemin+rainpassed2+(1|colony),
              bin~timemin+phase+(1|colony),
              bin~t.amb+rainpassed2+(1|colony),
               bin~t.amb+phase+(1|colony),
              bin~rainpassed2+phase+(1|colony),
              bin~timemin+t.amb+rainpassed2+(1|colony),
              bin~timemin+t.amb+phase+(1|colony),
              bin~t.amb+rainpassed2+phase+(1|colony),
              bin~timemin+t.amb+rainpassed2+phase+(1|colony))


fits <- map(models, glmer,family=binomial, data=chela)
aic <- map_dbl(fits,AIC)
aic
which.min(aic)
models[[which.min(aic)]] 


# None of the variables contribute to the model


# Other way to test for the model that best explain the data, with information on the weight of the model
fe <- c("1", "timemin", "t.amb", "rainpassed2", "phase",
        "timemin+t.amb",
              "timemin+rainpassed2",
              "timemin+phase",
              "t.amb+rainpassed2",
               "t.amb+phase",
              "rainpassed2+phase",
               "timemin+t.amb+rainpassed2",
               "timemin+t.amb+phase",
              "t.amb+rainpassed2+phase",
              "timemin+t.amb+rainpassed2+phase")

re <- c("(1 | colony)")
forms <- expand.grid(LHS = "bin ~", fe = fe, re = re)
models <- forms %>% mutate(RHS = paste(fe, re, sep = "+"), model = paste(LHS, RHS), 
    fits = map(model, ~glmer(as.formula(.x), data = chela, family = binomial)))

models <- mutate(models, converged = !map_lgl(fits, ~length(.x@optinfo$conv$lme4) > 
    0))
which(!models$converged) # Models that had convergence issues

pander(model.sel(models$fits))


summary(models$fit[[1]])

#None of the variables contribute to the model better do a descritive plot
```

### Peeking out
```{r}
peek<-databinb%>%filter(beh=="S")
sum(peek$bin)
nrow(peek)

b1<-glm(bin~timemin+t.amb+rainpassed2+phase, data=peek, family=binomial)
summary(b1)

b1<-glmer(bin~timemin+t.amb+rainpassed2+phase+(1|colony), data=peek, family=binomial)
summary(b1)

# Checking the if the results change if doing it by colony
peekbci5<-databinb%>%filter(beh=="S") %>% filter(colony=="BCI5")

b1<-glm(bin~timemin+t.amb+rainpassed2+mlight+phase, data=peekbci5, family=binomial)
summary(b1)
b1<-glm(bin~timemin, data=peekbci5, family=binomial)
summary(b1)

peekbci6<-databinb%>%filter(beh=="S") %>% filter(colony=="BCI6")

b1<-glm(bin~timemin+t.amb+rainpassed2+mlight+phase, data=peekbci6, family=binomial)
summary(b1)
b1<-glm(bin~timemin, data=peekbci6, family=binomial)
summary(b1)


b1<-glmer(bin~timemin+t.amb+rainpassed2+phase+(1|colony), data=peek, family=binomial)
summary(b1)

# Checking residuals
library(statmod)
library(broom.mixed)
residb1 <- augment(b1)
qres.binom <- function(glmer.obj) {
    p <- fitted(glmer.obj)
    y <- glmer.obj@resp$y
    if (!is.null(glmer.obj@resp$weights)) 
        n <- glmer.obj@resp$weights else n <- rep(1, length(y))
    y <- n * y
    a <- pbinom(y - 1, n, p)
    b <- pbinom(y, n, p)
    u <- runif(n = length(y), min = a, max = b)
    qnorm(u)
}
residb1$qr <- qres.binom(b1)

ggplot(residb1, aes(x = .fitted, y = qr)) + geom_point() + geom_smooth() + geom_hline(yintercept = 0, 
    linetype = 2)

probs <- c(0.25, 0.75)
y <- quantile(residb1$qr, probs, names = FALSE, na.rm = TRUE)
x <- qnorm(probs)
slope <- diff(y)/diff(x)
int <- y[1L] - slope * x[1L]
ggplot(residb1, aes(sample = qr)) + geom_qq(size = rel(4)) + geom_abline(intercept = int, 
    slope = slope, linetype = 2, size = 2)

ggplot(residb1, aes(x = .fitted, y = sqrt(abs(qr)))) + geom_point() + geom_smooth() + 
    geom_hline(yintercept = 1)

ggplot(residb1, aes(x = timemin, y = qr)) + geom_point() + geom_smooth() + geom_hline(yintercept = 0, 
    linetype = 2)
ggplot(residb1, aes(x = t.amb, y = qr)) + geom_point() + geom_smooth() + geom_hline(yintercept = 0, 
    linetype = 2)
ggplot(residb1, aes(x = rainpassed2, y = qr)) + geom_point() + geom_smooth() + geom_hline(yintercept = 0, 
    linetype = 2)
ggplot(residb1, aes(x = mlight, y = qr)) + geom_point() + geom_smooth() + geom_hline(yintercept = 0, 
    linetype = 2)
ggplot(residb1, aes(x = phase, y = qr)) + geom_point() + geom_smooth() + geom_hline(yintercept = 0, 
    linetype = 2)

# Plotting model predictions
plot_model(b1, type = "pred", terms=c("timemin"), show.data=T, show.p=T, show.values = T, axis.lim = c(0,1))  +
  labs(x = "Time of day (min)", y = "Predicted Probability of Peeking out", title = NULL) +
  theme_classic(base_size = 18)
ggsave("Plots/Presence Absence behaviors/PABCI_peek_timemin.png",plot = last_plot(),width=8, height=6, units="in" )

plot_model(b1, type = "pred", terms=c( "t.amb"), show.data=T, show.p=T, show.values = T, axis.lim = c(0,1))  +
  labs(x = "Temperature (°C)", y = "Predicted Probability of Peeking out", title = NULL) +
  theme_classic(base_size = 18)
ggsave("Plots/Presence Absence behaviors/PABCI_peek_temp.png",plot = last_plot(),width=8, height=6, units="in" )

plot_model(b1, type = "pred", terms=c( "rainpassed2"), show.data=T, show.p=T, show.values = T, axis.lim = c(0,1))  +
  labs(x = "Hours since last rain", y = "Predicted Probability of Peeking out", title = NULL) +
  theme_classic(base_size = 18)
ggsave("Plots/Presence Absence behaviors/PABCI_peek_rain.png",plot = last_plot(),width=8, height=6, units="in" )

plot_model(b1, type = "pred", terms=c( "mlight"), show.data=T, show.p=T, show.values = T, axis.lim = c(0,1))  +
  labs(x = "Presence of moonlight", y = "Predicted Probability of Peeking out", title = NULL) +
  theme_classic(base_size = 18)
ggsave("Plots/Presence Absence behaviors/PABCI_peek_light.png",plot = last_plot(),width=8, height=6, units="in" )

plot_model(b1, type = "pred", terms=c( "phase"), show.data=T, show.p=T, show.values = T, axis.lim = c(0,1))  +
  labs(x = "Moon phase", y = "Predicted Probability of Peeking out", title = NULL) +
  theme_classic(base_size = 18)
ggsave("Plots/Presence Absence behaviors/PABCI_peek_phase.png",plot = last_plot(),width=8, height=6, units="in" )

# checking which variables contribute more to the model
models <- list(bin~1+(1|colony),
              bin~timemin+(1|colony),
              bin~t.amb+(1|colony),
              bin~rainpassed2+(1|colony),
              bin~phase+(1|colony),
              bin~timemin+t.amb+(1|colony),
              bin~timemin+rainpassed2+(1|colony),
              bin~timemin+phase+(1|colony),
              bin~t.amb+rainpassed2+(1|colony),
               bin~t.amb+phase+(1|colony),
              bin~rainpassed2+phase+(1|colony),
              bin~timemin+t.amb+rainpassed2+(1|colony),
              bin~timemin+t.amb+phase+(1|colony),
              bin~t.amb+rainpassed2+phase+(1|colony),
              bin~timemin+t.amb+rainpassed2+phase+(1|colony))


fits <- map(models, glmer,family=binomial, data=peek)
aic <- map_dbl(fits,AIC)
aic
which.min(aic)
models[[which.min(aic)]] 



# All the variables contribute to the model


# Other way to test for the model that best explain the data, with information on the weight of the model
fe <- c("1", "timemin", "t.amb", "rainpassed2", "phase",
        "timemin+t.amb",
              "timemin+rainpassed2",
              "timemin+phase",
              "t.amb+rainpassed2",
               "t.amb+phase",
              "rainpassed2+phase",
               "timemin+t.amb+rainpassed2",
               "timemin+t.amb+phase",
              "t.amb+rainpassed2+phase",
              "timemin+t.amb+rainpassed2+phase")

re <- c("(1 | colony)")
forms <- expand.grid(LHS = "bin ~", fe = fe, re = re)
models <- forms %>% mutate(RHS = paste(fe, re, sep = "+"), model = paste(LHS, RHS), 
    fits = map(model, ~glmer(as.formula(.x), data = peek, family = binomial)))

models <- mutate(models, converged = !map_lgl(fits, ~length(.x@optinfo$conv$lme4) > 
    0))
which(!models$converged) # Models that had convergence issues

pander(model.sel(models$fits))

summary(models$fit[[13]])



```


### Feeding

There were only 6 events where we saw them feeding, better to leave it as descriptive

```{r}
feed<-databinb%>%filter(beh=="A")
feed$rainpassed3<-as.numeric(feed$rainpassed2)
summary(feed)


b1<-glm(bin~timemin+t.amb+rainpassed2+mlight+phase, data=feed, family=binomial) 
summary(b1)

b1<-glm(bin~timemin, data=feed, family=binomial) 
summary(b1)

b1<-glmer(bin~timemin+t.amb+rainpassed2+mlight+phase+(1|colony), data=feed, family=binomial) 
summary(b1)

# Checking the if the results change if doing it by colony
feedbci5<-databinb%>%filter(beh=="A") %>% filter(colony=="BCI5")

b1<-glm(bin~timemin+t.amb+rainpassed2+mlight+phase, data=feedbci5, family=binomial)
summary(b1)
b1<-glm(bin~timemin, data=feedbci5, family=binomial)
summary(b1)

feedbci6<-databinb%>%filter(beh=="A") %>% filter(colony=="BCI6")

b1<-glm(bin~timemin+t.amb+rainpassed2+mlight+phase, data=feedbci6, family=binomial)
summary(b1)
b1<-glm(bin~timemin, data=feedbci6, family=binomial)
summary(b1)

b1<-glmer(bin~timemin+t.amb+rainpassed2+mlight+phase+(1|colony), data=feed, family=binomial) 
summary(b1)

# Checking residuals
library(statmod)
library(broom.mixed)
residb1 <- augment(b1)
qres.binom <- function(glmer.obj) {
    p <- fitted(glmer.obj)
    y <- glmer.obj@resp$y
    if (!is.null(glmer.obj@resp$weights)) 
        n <- glmer.obj@resp$weights else n <- rep(1, length(y))
    y <- n * y
    a <- pbinom(y - 1, n, p)
    b <- pbinom(y, n, p)
    u <- runif(n = length(y), min = a, max = b)
    qnorm(u)
}
residb1$qr <- qres.binom(b1)

ggplot(residb1, aes(x = .fitted, y = qr)) + geom_point() + geom_smooth() + geom_hline(yintercept = 0, 
    linetype = 2)

probs <- c(0.25, 0.75)
y <- quantile(residb1$qr, probs, names = FALSE, na.rm = TRUE)
x <- qnorm(probs)
slope <- diff(y)/diff(x)
int <- y[1L] - slope * x[1L]
ggplot(residb1, aes(sample = qr)) + geom_qq(size = rel(4)) + geom_abline(intercept = int, 
    slope = slope, linetype = 2, size = 2)

ggplot(residb1, aes(x = .fitted, y = sqrt(abs(qr)))) + geom_point() + geom_smooth() + 
    geom_hline(yintercept = 1)

ggplot(residb1, aes(x = timemin, y = qr)) + geom_point() + geom_smooth() + geom_hline(yintercept = 0, 
    linetype = 2)
ggplot(residb1, aes(x = t.amb, y = qr)) + geom_point() + geom_smooth() + geom_hline(yintercept = 0, 
    linetype = 2)
ggplot(residb1, aes(x = rainpassed2, y = qr)) + geom_point() + geom_smooth() + geom_hline(yintercept = 0, 
    linetype = 2)
ggplot(residb1, aes(x = mlight, y = qr)) + geom_point() + geom_smooth() + geom_hline(yintercept = 0, 
    linetype = 2)
ggplot(residb1, aes(x = phase, y = qr)) + geom_point() + geom_smooth() + geom_hline(yintercept = 0, 
    linetype = 2)

# Plotting model predictions
plot_model(b1, type = "pred", terms=c("timemin"), show.data=T, show.p=T, show.values = T, axis.lim = c(0,1))  +
  labs(x = "Time of day (min)", y = "Predicted Probability of Feeding", title = NULL) +
  theme_classic(base_size = 18)
ggsave("Plots/Presence Absence behaviors/PA_feed_timemin.png",plot = last_plot(),width=8, height=6, units="in" )

plot_model(b1, type = "pred", terms=c( "t.amb"), show.data=T, show.p=T, show.values = T, axis.lim = c(0,1))  +
  labs(x = "Temperature (°C)", y = "Predicted Probability of Feeding", title = NULL) +
  theme_classic(base_size = 18)
ggsave("Plots/Presence Absence behaviors/PA_feed_temp.png",plot = last_plot(),width=8, height=6, units="in" )

plot_model(b1, type = "pred", terms=c( "rainpassed2"), show.data=T, show.p=T, show.values = T, axis.lim = c(0,1))  +
  labs(x = "Hours since last rain", y = "Predicted Probability of Feeding", title = NULL) +
  theme_classic(base_size = 18)
ggsave("Plots/Presence Absence behaviors/PA_feed_rain.png",plot = last_plot(),width=8, height=6, units="in" )

plot_model(b1, type = "pred", terms=c( "mlight"), show.data=T, show.p=T, show.values = T, axis.lim = c(0,1))  +
  labs(x = "Presence of moonlight", y = "Predicted Probability of Feeding", title = NULL) +
  theme_classic(base_size = 18)
ggsave("Plots/Presence Absence behaviors/PA_feed_light.png",plot = last_plot(),width=8, height=6, units="in" )

plot_model(b1, type = "pred", terms=c( "phase"), show.data=T, show.p=T, show.values = T, axis.lim = c(0,1))  +
  labs(x = "Moon phase", y = "Predicted Probability of Feeding", title = NULL) +
  theme_classic(base_size = 18)
ggsave("Plots/Presence Absence behaviors/PA_feed_phase.png",plot = last_plot(),width=8, height=6, units="in" )

# checking which variables contribute more to the model
models <- list(bin~1+(1|colony),
              bin~timemin+(1|colony),
              bin~t.amb+(1|colony),
              bin~rainpassed2+(1|colony),
              bin~mlight+(1|colony),
              bin~phase+(1|colony),
              bin~timemin+t.amb+(1|colony),
              bin~timemin+rainpassed2+(1|colony),
              bin~timemin+mlight+(1|colony),
              bin~timemin+phase+(1|colony),
              bin~t.amb+rainpassed2+(1|colony),
               bin~t.amb+mlight+(1|colony),
               bin~t.amb+phase+(1|colony),
              bin~rainpassed2+mlight+(1|colony),
              bin~rainpassed2+phase+(1|colony),
              bin~mlight+phase+(1|colony),
               bin~timemin+t.amb+rainpassed2+(1|colony),
               bin~timemin+t.amb+mlight+(1|colony),
               bin~timemin+t.amb+phase+(1|colony),
              bin~t.amb+rainpassed2+mlight+(1|colony),
              bin~t.amb+rainpassed2+phase+(1|colony),
               bin~rainpassed2+mlight+phase+(1|colony),
              bin~t.amb+rainpassed2+mlight+phase+(1|colony),
              bin~timemin+rainpassed2+mlight+phase+(1|colony),
              bin~timemin+t.amb+mlight+phase+(1|colony),
              bin~timemin+t.amb+rainpassed2+phase+(1|colony),
              bin~timemin+t.amb+rainpassed2+mlight+(1|colony),
              bin~timemin+t.amb+rainpassed2+mlight+phase+(1|colony))


fits <- map(models, glmer,family=binomial, data=feed)
aic <- map_dbl(fits,AIC)
aic
which.min(aic)
models[[which.min(aic)]] 

# Model with the variables that most contribute to the model
b2<-glmer(bin~mlight+(1|colony), data=feed, family=binomial)
summary(b2)




# Other way to test for the model that best explain the data, with information on the weight of the model
fe <- c("1", "timemin", "t.amb", "rainpassed2", "mlight", "phase",
        "timemin+t.amb",
              "timemin+rainpassed2",
              "timemin+mlight",
              "timemin+phase",
              "t.amb+rainpassed2",
               "t.amb+mlight",
               "t.amb+phase",
              "rainpassed2+mlight",
              "rainpassed2+phase",
              "mlight+phase",
               "timemin+t.amb+rainpassed2",
               "timemin+t.amb+mlight",
               "timemin+t.amb+phase",
              "t.amb+rainpassed2+mlight",
              "t.amb+rainpassed2+phase",
               "rainpassed2+mlight+phase",
              "t.amb+rainpassed2+mlight+phase",
              "timemin+rainpassed2+mlight+phase",
              "timemin+t.amb+mlight+phase",
              "timemin+t.amb+rainpassed2+phase",
              "timemin+t.amb+rainpassed2+mlight",
              "timemin+t.amb+rainpassed2+mlight+phase")

re <- c("(1 | colony)")
forms <- expand.grid(LHS = "bin ~", fe = fe, re = re)
models <- forms %>% mutate(RHS = paste(fe, re, sep = "+"), model = paste(LHS, RHS), 
    fits = map(model, ~glmer(as.formula(.x), data = feed, family = binomial)))

models <- mutate(models, converged = !map_lgl(fits, ~length(.x@optinfo$conv$lme4) > 
    0))
which(!models$converged) # Models that had convergence issues

pander(model.sel(models$fits))



summary(models$fit[[5]])

```

### Outside2: merging outside and walking

There are not enough data to test for outside and walking on BCI (18 out of 194 observations), better leave it as descriptive

```{r}
out<-databinb%>%filter(grepl("F|C", beh))
sum(out$bin)
nrow(out)

b1<-glm(bin~timemin, data=out, family=binomial)
summary(b1)


b1<-glmer(bin~timemin+t.amb+rainpassed2+mlight+phase+(1|colony), data=out, family=binomial)
summary(b1)

# Checking residuals
library(statmod)
library(broom.mixed)
residb1 <- augment(b1)
qres.binom <- function(glmer.obj) {
    p <- fitted(glmer.obj)
    y <- glmer.obj@resp$y
    if (!is.null(glmer.obj@resp$weights)) 
        n <- glmer.obj@resp$weights else n <- rep(1, length(y))
    y <- n * y
    a <- pbinom(y - 1, n, p)
    b <- pbinom(y, n, p)
    u <- runif(n = length(y), min = a, max = b)
    qnorm(u)
}
residb1$qr <- qres.binom(b1)

ggplot(residb1, aes(x = .fitted, y = qr)) + geom_point() + geom_smooth() + geom_hline(yintercept = 0, 
    linetype = 2)

probs <- c(0.25, 0.75)
y <- quantile(residb1$qr, probs, names = FALSE, na.rm = TRUE)
x <- qnorm(probs)
slope <- diff(y)/diff(x)
int <- y[1L] - slope * x[1L]
ggplot(residb1, aes(sample = qr)) + geom_qq(size = rel(4)) + geom_abline(intercept = int, 
    slope = slope, linetype = 2, size = 2)

ggplot(residb1, aes(x = .fitted, y = sqrt(abs(qr)))) + geom_point() + geom_smooth() + 
    geom_hline(yintercept = 1)

ggplot(residb1, aes(x = timemin, y = qr)) + geom_point() + geom_smooth() + geom_hline(yintercept = 0, 
    linetype = 2)
ggplot(residb1, aes(x = t.amb, y = qr)) + geom_point() + geom_smooth() + geom_hline(yintercept = 0, 
    linetype = 2)
ggplot(residb1, aes(x = rainpassed2, y = qr)) + geom_point() + geom_smooth() + geom_hline(yintercept = 0, 
    linetype = 2)
ggplot(residb1, aes(x = mlight, y = qr)) + geom_point() + geom_smooth() + geom_hline(yintercept = 0, 
    linetype = 2)
ggplot(residb1, aes(x = phase, y = qr)) + geom_point() + geom_smooth() + geom_hline(yintercept = 0, 
    linetype = 2)

# Plotting model predictions
plot_model(b1, type = "pred", terms=c("timemin"), show.data=T, show.p=T, show.values = T, axis.lim = c(0,1))  +
  labs(x = "Time of day (min)", y = "Predicted Probability of being outside", title = NULL) +
  theme_classic(base_size = 18)
ggsave("Plots/Presence Absence behaviors/PA_out_timemin.png",plot = last_plot(),width=8, height=6, units="in" )

plot_model(b1, type = "pred", terms=c( "t.amb"), show.data=T, show.p=T, show.values = T, axis.lim = c(0,1))  +
  labs(x = "Temperature (°C)", y = "Predicted Probability of being outside", title = NULL) +
  theme_classic(base_size = 18)
ggsave("Plots/Presence Absence behaviors/PA_out_temp.png",plot = last_plot(),width=8, height=6, units="in" )

plot_model(b1, type = "pred", terms=c( "rainpassed2"), show.data=T, show.p=T, show.values = T, axis.lim = c(0,1))  +
  labs(x = "Hours since last rain", y = "Predicted Probability of being outside", title = NULL) +
  theme_classic(base_size = 18)
ggsave("Plots/Presence Absence behaviors/PA_out_rain.png",plot = last_plot(),width=8, height=6, units="in" )

plot_model(b1, type = "pred", terms=c( "mlight"), show.data=T, show.p=T, show.values = T, axis.lim = c(0,1))  +
  labs(x = "Presence of moonlight", y = "Predicted Probability of being outside", title = NULL) +
  theme_classic(base_size = 18)
ggsave("Plots/Presence Absence behaviors/PA_out_light.png",plot = last_plot(),width=8, height=6, units="in" )

plot_model(b1, type = "pred", terms=c( "phase"), show.data=T, show.p=T, show.values = T, axis.lim = c(0,1))  +
  labs(x = "Moon phase", y = "Predicted Probability of being outside", title = NULL) +
  theme_classic(base_size = 18)
ggsave("Plots/Presence Absence behaviors/PA_out_phase.png",plot = last_plot(),width=8, height=6, units="in" )

# checking which variables contribute more to the model
models <- list(bin~1+(1|colony),
              bin~timemin+(1|colony),
              bin~t.amb+(1|colony),
              bin~rainpassed2+(1|colony),
              bin~mlight+(1|colony),
              bin~phase+(1|colony),
              bin~timemin+t.amb+(1|colony),
              bin~timemin+rainpassed2+(1|colony),
              bin~timemin+mlight+(1|colony),
              bin~timemin+phase+(1|colony),
              bin~t.amb+rainpassed2+(1|colony),
               bin~t.amb+mlight+(1|colony),
               bin~t.amb+phase+(1|colony),
              bin~rainpassed2+mlight+(1|colony),
              bin~rainpassed2+phase+(1|colony),
              bin~mlight+phase+(1|colony),
               bin~timemin+t.amb+rainpassed2+(1|colony),
               bin~timemin+t.amb+mlight+(1|colony),
               bin~timemin+t.amb+phase+(1|colony),
              bin~t.amb+rainpassed2+mlight+(1|colony),
              bin~t.amb+rainpassed2+phase+(1|colony),
               bin~rainpassed2+mlight+phase+(1|colony),
              bin~t.amb+rainpassed2+mlight+phase+(1|colony),
              bin~timemin+rainpassed2+mlight+phase+(1|colony),
              bin~timemin+t.amb+mlight+phase+(1|colony),
              bin~timemin+t.amb+rainpassed2+phase+(1|colony),
              bin~timemin+t.amb+rainpassed2+mlight+(1|colony),
              bin~timemin+t.amb+rainpassed2+mlight+phase+(1|colony))


fits <- map(models, glmer,family=binomial, data=out)
aic <- map_dbl(fits,AIC)
aic
which.min(aic)
models[[which.min(aic)]] 

# Model with the variables that most contribute to the model
b2<-glmer(bin~ rainpassed2 + mlight + phase + +(1|colony), data=out, family=binomial)
summary(b2)



# Other way to test for the model that best explain the data, with information on the weight of the model
fe <- c("1", "timemin", "t.amb", "rainpassed2", "mlight", "phase",
        "timemin+t.amb",
              "timemin+rainpassed2",
              "timemin+mlight",
              "timemin+phase",
              "t.amb+rainpassed2",
               "t.amb+mlight",
               "t.amb+phase",
              "rainpassed2+mlight",
              "rainpassed2+phase",
              "mlight+phase",
               "timemin+t.amb+rainpassed2",
               "timemin+t.amb+mlight",
               "timemin+t.amb+phase",
              "t.amb+rainpassed2+mlight",
              "t.amb+rainpassed2+phase",
               "rainpassed2+mlight+phase",
              "t.amb+rainpassed2+mlight+phase",
              "timemin+rainpassed2+mlight+phase",
              "timemin+t.amb+mlight+phase",
              "timemin+t.amb+rainpassed2+phase",
              "timemin+t.amb+rainpassed2+mlight",
              "timemin+t.amb+rainpassed2+mlight+phase")

re <- c("(1 | colony)")
forms <- expand.grid(LHS = "bin ~", fe = fe, re = re)
models <- forms %>% mutate(RHS = paste(fe, re, sep = "+"), model = paste(LHS, RHS), 
    fits = map(model, ~glmer(as.formula(.x), data = out, family = binomial)))

models <- mutate(models, converged = !map_lgl(fits, ~length(.x@optinfo$conv$lme4) > 
    0))
which(!models$converged) # Models that had convergence issues

pander(model.sel(models$fits))


summary(models$fit[[22]]) 
```



## Looking at total amount of individuals per behavior (June only)
### Filtering data to only include june data
```{r}
# Total number of pseudoscorpions doing the activity
datajune<-data2 %>% drop_na(total) %>% 
  #dplyr::select(colony, location,t.amb, h.amb, phase, time, daytime, hour, Q, C, A, S, E, F, total) %>%
  pivot_longer(cols=(6:11), names_to = "beh" , values_to="inds") %>%
  mutate(prop=inds/total, 
         hour2=factor(hour,levels=c("20","21", "22", "23", "0", "1", "2", "3", "4")),
         bin=if_else(inds>0,1,0),
         beh2=case_when(beh=="A"~"Feeding",
                        beh=="C"~"Walking",
                        beh=="E"~"Hiding",
                        beh=="F"~"Outside",
                        beh=="Q"~"Chelaes exp.",
                        beh=="S"~"Peeking out",
                        TRUE~NA)) 



datajune$beh2<-factor(datajune$beh2, levels=c("Hiding", "Peeking out", "Walking", "Outside", "Chelaes exp.", "Feeding"))
str(datajune)
```


### Variation between behaviors
```{r}
ggplot(data=datajune, aes(y=inds, x=colony))+geom_boxplot()+geom_jitter(color="red", alpha=0.5)+facet_wrap(~beh2)
```

The behaviors with more variation are: feeding, hiding, chelaes exposed and peeking

Walking and standing outside did not have a lot of variation

# Doing amultinomial logistic regression with random effects
```{r}

m1<-mblogit(beh2~hour+t.amb+rainpassed2+mlight+phase, random=(~1|colony), weights=total, data = datajune, method=c("PQL"), estimator=c("ML"))
summary(m1)

coefs <- summary(m1)$coefficients
LLs <- coefs[,1] + qnorm(.025)*coefs[,2]
ULs <- coefs[,1] + qnorm(.975)*coefs[,2]
OR <- exp(coefs[,1])
ORLL <- exp(LLs)
ORUL <- exp(ULs)
HHES <- coefs[,1]/1.81 # Hasselblad and Hedges Effect Size


round(cbind(coefs, LLs, ULs), 3)


datajune2<-datajune %>% dplyr::select(colony, hour, t.amb, rainpassed2,mlight, phase, total, beh2, obsdaytime, inds) %>% uncount(inds)
str(datajune2)
datajune2$obsdaytime2<-as.factor(datajune2$obsdaytime)

m2<-mblogit(beh2~hour+t.amb+rainpassed2+mlight+phase, random=list(~1|colony, ~1|obsdaytime2), data = datajune2, method=c("PQL"), estimator=c("ML"))
summary(m2)

coefs <- summary(m2)$coefficients
LLs <- coefs[,1] + qnorm(.025)*coefs[,2]
ULs <- coefs[,1] + qnorm(.975)*coefs[,2]
OR <- exp(coefs[,1])
ORLL <- exp(LLs)
ORUL <- exp(ULs)
HHES <- coefs[,1]/1.81 # Hasselblad and Hedges Effect Size


round(cbind(coefs, LLs, ULs), 3)



```


### Chelaes exposed
```{r}
chela<-datajune%>%filter(beh=="Q")

ggplot(chela, aes(x=inds))+geom_histogram(binwidth = 1)

# GLMM with poisson
f1<-glmer(inds~hour+t.amb+rainpassed2+mlight+phase+(1|colony), data=chela, family=poisson)
summary(f1) #AIC 320.8 Deviance: 298.8 , resid df:59 

op<-par(mfrow=c(2,2), mar=c(5,4,1,2))
plot(f1, add.smooth=FALSE, which=1)
E<-resid(f1)
hist(E, xlab="Residuals", main="")
#plot(chela$hour, E, xlab="cycle", ylab="residuals")

plot_model(f1, type = "resid", show.data=T) 


# GLMM negative binomial
f2<-glmer.nb(inds~hour+t.amb+rainpassed2+mlight+phase+(1|colony), data=chela)
summary(f2) #AIC 317.6 Deviance: 297.6, resid df:60

m.glm <- glm.nb(inds ~ hour+t.amb+rainpassed2+mlight+phase, data=chela, trace=TRUE)
## The neg.binomial theta parameter:
getME(f2, "glmer.nb.theta")
LL <- logLik(f2)
## mixed model has 1 additional parameter (RE variance)
stopifnot(attr(LL,"df")==attr(logLik(m.glm),"df")+1)
#plot(f4a, resid(.) ~ g)# works, as long as data 'dd' is found

op<-par(mfrow=c(2,2), mar=c(5,4,1,2))
#plot(f4b, add.smooth=FALSE, which=1)
E<-resid(f2)
hist(E, xlab="Residuals", main="")

plot_model(f2, type = "resid", show.data=T) 



```






# Pasos: Probar modelo global (glm, o zero inflado, poisson o binom neg) y luego escoger variables (probar lista de modelos y ver cuales variabels aportan mas al modelo)



























# Analisis done before
## Per hour
```{r,eval=FALSE, include=FALSE}
ggplot(data=datajune, aes(x=hour,y=beh))+
  geom_density_ridges( jittered_points=T, scale=0.8)+
  theme_classic()

ggplot(datajune, aes(x=hour2, y=prop)) +geom_boxplot() +facet_wrap(~ beh2, scales="free_y")  + geom_jitter()
```


```{r}
#Number of occassions on which they were observed doing the behaviors
ggplot(datajune, aes(x=hour2, y=bin, fill=location)) +geom_bar(stat="identity") +facet_wrap(~ beh)


ggplot(datajune, aes(x=hour2, y=inds, fill=location, color=location)) +geom_point() +facet_grid(location~ beh, scales="free_y") 
ggplot(datajune, aes(x=hour, y=inds, fill=location)) +geom_bar(stat="identity") +facet_grid(location~ beh, scales="free_y")
ggplot(datajune, aes(x=hour, y=inds, fill=location)) +geom_bar(stat="identity") +facet_grid(beh~ location, scales="free_y")
ggplot(datajune, aes(x=hour, y=inds, fill=beh)) +geom_bar(stat="identity",position="fill") +facet_wrap(~ location)
```


```{r}
# Proportional number of pseudoscorpions doing the activity
ggplot(datajune, aes(x=as.factor(hour), y=prop, fill=location, color=location)) +geom_point() +facet_grid(location~ beh, scales="free_y")

ggplot(datajune, aes(x=daytime, y=inds, fill=location)) + geom_col() +facet_grid(location~ beh, scales="free")
ggplot(datajune, aes(x=hour, y=prop, fill=location)) +geom_bar(stat="identity") +facet_grid(beh~ location, scales="free_y")
```


```{r}
# Feeding
a<-datajune%>% filter(beh=="A")
a1<-ggplot(a, aes(x=hour2, y=prop)) +geom_boxplot() +geom_jitter(aes(color=location)) + theme_classic() + ylab("Proportion") + xlab("Hour")  +guides(color=guide_legend(title="Location"))
a2<-ggplot(a, aes(x=hour2, y=inds)) +geom_boxplot() +geom_jitter(aes(color=location)) + theme_classic() + ylab("Counts") + xlab("Hour") +guides(color=guide_legend(title="Location"))
ggarrange(a1,a2, ncol=1, common.legend = T, legend="bottom")
ggsave("Plots/activity_feeding.png", plot = last_plot(), width=6, heigh=4, units="in")
```


```{r}
# Chelaes
a<-datajune%>% filter(beh=="Q")
a1<-ggplot(a, aes(x=hour2, y=prop)) +geom_boxplot() +geom_jitter(aes(color=location)) + theme_classic() + ylab("Proportion") + xlab("Hour")  +guides(color=guide_legend(title="Location"))
a2<-ggplot(a, aes(x=hour2, y=inds)) +geom_boxplot() +geom_jitter(aes(color=location)) + theme_classic() + ylab("Counts") + xlab("Hour") +guides(color=guide_legend(title="Location"))
ggarrange(a1,a2, ncol=1, common.legend = T, legend="bottom")
ggsave("Plots/activity_chelaes.png", plot = last_plot(), width=6, heigh=4, units="in")
```


```{r}
# Walking
a<-datajune%>% filter(beh=="C")
a1<-ggplot(a, aes(x=hour2, y=prop)) +geom_boxplot() +geom_jitter(aes(color=location)) + theme_classic() + ylab("Proportion") + xlab("Hour")  +guides(color=guide_legend(title="Location"))
a2<-ggplot(a, aes(x=hour2, y=inds)) +geom_boxplot() +geom_jitter(aes(color=location)) + theme_classic() + ylab("Counts") + xlab("Hour") +guides(color=guide_legend(title="Location"))
ggarrange(a1,a2, ncol=1, common.legend = T, legend="bottom")
ggsave("Plots/activity_walking.png", plot = last_plot(), width=6, heigh=4, units="in")
```


```{r}
# Peeking out
a<-datajune%>% filter(beh=="S")
a1<-ggplot(a, aes(x=hour2, y=prop)) +geom_boxplot() +geom_jitter(aes(color=location)) + theme_classic() + ylab("Proportion") + xlab("Hour")  +guides(color=guide_legend(title="Location"))
a2<-ggplot(a, aes(x=hour2, y=inds)) +geom_boxplot() +geom_jitter(aes(color=location)) + theme_classic() + ylab("Counts") + xlab("Hour") +guides(color=guide_legend(title="Location"))
ggarrange(a1,a2, ncol=1, common.legend = T, legend="bottom")
ggsave("Plots/activity_peeking.png", plot = last_plot(), width=6, heigh=4, units="in")
```


```{r}
# Hiding
a<-datajune%>% filter(beh=="E")
a1<-ggplot(a, aes(x=hour2, y=prop)) +geom_boxplot() +geom_jitter(aes(color=location)) + theme_classic() + ylab("Proportion") + xlab("Hour")  +guides(color=guide_legend(title="Location"))
a2<-ggplot(a, aes(x=hour2, y=inds)) +geom_boxplot() +geom_jitter(aes(color=location)) + theme_classic() + ylab("Counts") + xlab("Hour") +guides(color=guide_legend(title="Location"))
ggarrange(a1,a2, ncol=1, common.legend = T, legend="bottom")
ggsave("Plots/activity_hiding.png", plot = last_plot(), width=6, heigh=4, units="in")

```


## Analizing walking data
```{r}
a<-datajune%>% filter(beh=="C")
ggplot(a, aes(x=hour, y=prop)) +geom_bar(stat="identity") + facet_wrap(~location)

ggplot(a, aes(x=daytime, y=prop)) +geom_point(stat="identity") + facet_wrap(~location, nrow=3)

#ggplot(data=a, aes(x=daytime,y=prop))+
 # geom_density_ridges(stat="identity", jittered_points=T, scale=0.8)+
  #theme_classic()

mod1<-glm(inds~t.amb+h.amb+phase+hour2+total, family = poisson, data =a)
summary(mod1)
sum.mod1 <- glance(mod1)
sum.mod1
gof.p.mod1 <- with(sum.mod1,pchisq(deviance,df.residual,lower=FALSE))
gof.p.mod1

# Checking assumptions
mod1.test <- augment(mod1)
lin.vor <- ggplot(mod1.test, aes(x = t.amb, y = .std.resid)) + geom_count() + 
  scale_size_area(max_size=4) + 
  geom_hline(yintercept = 0, linetype = 2) + 
  geom_smooth() + guides(size = FALSE)
lin.pc1 <- lin.vor + aes(x = h.amb)
lin.pc2 <- lin.vor + aes(x = phase)
lin.pc3 <- lin.vor + aes(x = hour2)
grid.arrange(lin.vor, lin.pc1, lin.pc2, lin.pc3)
# all seems to be within the acceptable range (do not differ from 0)
# Checking residual plots:
resd1 <- ggplot(mod1.test, aes(x = .fitted, y = .resid)) + 
  geom_point() + 
  geom_smooth() + 
  geom_hline(yintercept = 0, linetype=2) 

resd2 <- resd1 + aes(y = sqrt(abs(.std.resid))) +
  geom_hline(yintercept = 1, linetype=2)

resd3 <- ggplot(mod1.test, aes(.hat, .std.resid)) +
 geom_vline(size = 2, colour = "white", xintercept = 0) +
  geom_hline(size = 2, colour = "white", yintercept = 0) +
  geom_point(aes(size = .cooksd)) + geom_smooth(se = FALSE) 

# get int and slope for qqline
probs <- c(0.25,0.75)
y <- quantile(mod1.test$.std.resid, probs, names = FALSE, na.rm = TRUE)
x <- qnorm(probs)
slope <- diff(y)/diff(x)
int <- y[1L] - slope * x[1L]

qq.mod <- ggplot(mod1.test, aes(sample=.std.resid)) + 
  geom_qq(size=rel(4)) + 
  geom_abline(intercept = int, slope = slope, linetype = 2, size = 2) 

grid.arrange(resd1, resd2, resd3, qq.mod)

# The residuals look overdispersed

# trying adding a random factor to the poisson distribution
mod2<-glmmPQL(inds~t.amb+h.amb+phase+hour2, random=~1|total, family = poisson, data =a)
summary(mod2)

op<-par(mfrow=c(2,2), mar=c(5,4,1,2))
plot(mod2, add.smooth=FALSE, which=1)
E<-resid(mod2)
hist(E, xlab="Residuals", main="")
plot(a$t.amb, E, xlab="Temperature", ylab="residuals")
plot(a$h.amb, E, xlab="Humidity", ylab="residuals")
plot(a$phase, E, xlab="Phase", ylab="residuals")
plot(a$hour2, E, xlab="Hour", ylab="residuals")

# The residuals do not look good.

#Trying negavitve binomial distribution
mod3<-glm.nb(inds~t.amb+h.amb+phase+hour+total, data =a)
summary(mod3)

op<-par(mfrow=c(2,2), mar=c(5,4,1,2))
plot(mod3, add.smooth=FALSE, which=1)
E<-resid(mod2)
hist(E, xlab="Residuals", main="")
plot(a$t.amb, E, xlab="Temperature", ylab="residuals")
plot(a$h.amb, E, xlab="Humidity", ylab="residuals")
plot(a$phase, E, xlab="Phase", ylab="residuals")
plot(a$hour2, E, xlab="Hour", ylab="residuals")
 
# The residuals do not look good.

#Trying adding a random factor with a negative binomial distribution
mod4<-glmmPQL(inds~t.amb+h.amb+phase+hour2, data=a, random = ~ 1 | total, family = negative.binomial (theta =  0.671, link = log))
summary(mod4)

op<-par(mfrow=c(2,2), mar=c(5,4,1,2))
plot(mod4, add.smooth=FALSE, which=1)
E<-resid(mod4)
hist(E, xlab="Residuals", main="")
plot(a$t.amb, E, xlab="Temperature", ylab="residuals")
plot(a$h.amb, E, xlab="Humidity", ylab="residuals")
plot(a$phase, E, xlab="Phase", ylab="residuals")
plot(a$hour2, E, xlab="Hour", ylab="residuals")

# The residuals do not look good.

# Trying a zero inflated analysis with Poisson distribution
Zip1<-zeroinfl(inds~t.amb+phase+hour+total|t.amb+phase+hour+total, dist= "poisson", link = "logit", data=a)
summary(Zip1)

mnull <- update(Zip1, . ~ 1)
summary(mnull)
pchisq(2 * (logLik(Zip1) - logLik(mnull)), df = 3, lower.tail = FALSE)

op<-par(mfrow=c(2,2), mar=c(5,4,1,2))
#plot(Zip1, add.smooth=FALSE, which=1)
E<-resid(Zip1)
hist(E, xlab="Residuals", main="")
plot(a$t.amb, E, xlab="Temperature", ylab="residuals")
plot(a$h.amb, E, xlab="Humidity", ylab="residuals")
plot(a$phase, E, xlab="Phase", ylab="residuals")
plot(a$hour, E, xlab="Hour", ylab="residuals")
plot(a$total, E, xlab="Total", ylab="residuals")

# The residulas look closer to zero and less overdispersed, lets try a zero inflated with a negative binomial distribution
Zip3<-zeroinfl(inds~t.amb+h.amb+phase+total+hour|t.amb+h.amb+phase+total+hour, dist= "negbin", link = "logit", data=a)
summary(Zip3)

op<-par(mfrow=c(2,2), mar=c(5,4,1,2))
#plot(Zip3, add.smooth=FALSE, which=1)
E<-resid(Zip3)
hist(E, xlab="Residuals", main="")
plot(a$t.amb, E, xlab="Temperature", ylab="residuals")
plot(a$h.amb, E, xlab="Humidity", ylab="residuals")
plot(a$phase, E, xlab="Phase", ylab="residuals")
plot(a$hour, E, xlab="Hour", ylab="residuals")
plot(a$total, E, xlab="total", ylab="residuals")

# The residuals are a bit less over dispersed than before, I think this one works best

#Final model
summary(Zip3)

```

## Analizing chelae data
```{r}
a<-datajune%>% filter(beh=="Q")
ggplot(a, aes(x=hour, y=prop)) +geom_bar(stat="identity") + facet_wrap(~location)

ggplot(a, aes(x=daytime, y=prop)) +geom_point(stat="identity") + facet_wrap(~location, nrow=3)

#ggplot(data=a, aes(x=daytime,y=prop))+
 # geom_density_ridges(stat="identity", jittered_points=T, scale=0.8)+
  #theme_classic()

mod1<-glm(inds~t.amb+h.amb+phase+hour2+total, family = poisson, data =a)
summary(mod1)
sum.mod1 <- glance(mod1)
sum.mod1
gof.p.mod1 <- with(sum.mod1,pchisq(deviance,df.residual,lower=FALSE))
gof.p.mod1

# Checking assumptions
mod1.test <- augment(mod1)
lin.vor <- ggplot(mod1.test, aes(x = t.amb, y = .std.resid)) + geom_count() + 
  scale_size_area(max_size=4) + 
  geom_hline(yintercept = 0, linetype = 2) + 
  geom_smooth() + guides(size = FALSE)
lin.pc1 <- lin.vor + aes(x = h.amb)
lin.pc2 <- lin.vor + aes(x = phase)
lin.pc3 <- lin.vor + aes(x = hour2)
grid.arrange(lin.vor, lin.pc1, lin.pc2, lin.pc3)
# all seems to be within the acceptable range (do not differ from 0)
# Checking residual plots:
resd1 <- ggplot(mod1.test, aes(x = .fitted, y = .resid)) + 
  geom_point() + 
  geom_smooth() + 
  geom_hline(yintercept = 0, linetype=2) 

resd2 <- resd1 + aes(y = sqrt(abs(.std.resid))) +
  geom_hline(yintercept = 1, linetype=2)

resd3 <- ggplot(mod1.test, aes(.hat, .std.resid)) +
 geom_vline(size = 2, colour = "white", xintercept = 0) +
  geom_hline(size = 2, colour = "white", yintercept = 0) +
  geom_point(aes(size = .cooksd)) + geom_smooth(se = FALSE) 

# get int and slope for qqline
probs <- c(0.25,0.75)
y <- quantile(mod1.test$.std.resid, probs, names = FALSE, na.rm = TRUE)
x <- qnorm(probs)
slope <- diff(y)/diff(x)
int <- y[1L] - slope * x[1L]

qq.mod <- ggplot(mod1.test, aes(sample=.std.resid)) + 
  geom_qq(size=rel(4)) + 
  geom_abline(intercept = int, slope = slope, linetype = 2, size = 2) 

grid.arrange(resd1, resd2, resd3, qq.mod)

# The residuals look overdispersed

# trying adding a random factor to the poisson distribution
mod2<-glmmPQL(inds~t.amb+h.amb+phase+hour2, random=~1|total, family = poisson, data =a)
summary(mod2)

op<-par(mfrow=c(2,2), mar=c(5,4,1,2))
plot(mod2, add.smooth=FALSE, which=1)
E<-resid(mod2)
hist(E, xlab="Residuals", main="")
plot(a$t.amb, E, xlab="Temperature", ylab="residuals")
plot(a$h.amb, E, xlab="Humidity", ylab="residuals")
plot(a$phase, E, xlab="Phase", ylab="residuals")
plot(a$hour2, E, xlab="Hour", ylab="residuals")

# The residuals do not look good.

#Trying negavitve binomial distribution
mod3<-glm.nb(inds~t.amb+h.amb+phase+hour+total, data =a)
summary(mod3)

op<-par(mfrow=c(2,2), mar=c(5,4,1,2))
plot(mod3, add.smooth=FALSE, which=1)
E<-resid(mod2)
hist(E, xlab="Residuals", main="")
plot(a$t.amb, E, xlab="Temperature", ylab="residuals")
plot(a$h.amb, E, xlab="Humidity", ylab="residuals")
plot(a$phase, E, xlab="Phase", ylab="residuals")
plot(a$hour2, E, xlab="Hour", ylab="residuals")
 
# The residuals do not look good.

#Trying adding a random factor with a negative binomial distribution
mod4<-glmmPQL(inds~t.amb+h.amb+phase+hour2, data=a, random = ~ 1 | total, family = negative.binomial (theta =  0.671, link = log))
summary(mod4)

op<-par(mfrow=c(2,2), mar=c(5,4,1,2))
plot(mod4, add.smooth=FALSE, which=1)
E<-resid(mod4)
hist(E, xlab="Residuals", main="")
plot(a$t.amb, E, xlab="Temperature", ylab="residuals")
plot(a$h.amb, E, xlab="Humidity", ylab="residuals")
plot(a$phase, E, xlab="Phase", ylab="residuals")
plot(a$hour2, E, xlab="Hour", ylab="residuals")

# The residuals do not look good.

# Trying a zero inflated analysis with Poisson distribution
Zip1<-zeroinfl(inds~t.amb+phase+hour+total|t.amb+phase+hour+total, dist= "poisson", link = "logit", data=a)
summary(Zip1)

mnull <- update(Zip1, . ~ 1)
summary(mnull)
pchisq(2 * (logLik(Zip1) - logLik(mnull)), df = 3, lower.tail = FALSE)

op<-par(mfrow=c(2,2), mar=c(5,4,1,2))
#plot(Zip1, add.smooth=FALSE, which=1)
E<-resid(Zip1)
hist(E, xlab="Residuals", main="")
plot(a$t.amb, E, xlab="Temperature", ylab="residuals")
plot(a$h.amb, E, xlab="Humidity", ylab="residuals")
plot(a$phase, E, xlab="Phase", ylab="residuals")
plot(a$hour, E, xlab="Hour", ylab="residuals")
plot(a$total, E, xlab="Total", ylab="residuals")

# The residulas look closer to zero and less overdispersed, lets try a zero inflated with a negative binomial distribution
Zip3<-zeroinfl(inds~t.amb+h.amb+phase+total+hour|t.amb+h.amb+phase+total+hour, dist= "negbin", link = "logit", data=a)
summary(Zip3)

op<-par(mfrow=c(2,2), mar=c(5,4,1,2))
#plot(Zip3, add.smooth=FALSE, which=1)
E<-resid(Zip3)
hist(E, xlab="Residuals", main="")
plot(a$t.amb, E, xlab="Temperature", ylab="residuals")
plot(a$h.amb, E, xlab="Humidity", ylab="residuals")
plot(a$phase, E, xlab="Phase", ylab="residuals")
plot(a$hour, E, xlab="Hour", ylab="residuals")
plot(a$total, E, xlab="total", ylab="residuals")

# The residuals are a bit less overdispersed than before, I think this one works best

# Adding colony ID as a random factor to the zero inflated model with Poisson distribution
Zip4<- glmmadmb (inds~t.amb+h.amb+phase+total+hour+ (1|colony), data = a, zeroInflation = TRUE, family = "poisson")
summary(Zip4)

op<-par(mfrow=c(2,2), mar=c(5,4,1,2))
#plot(Zip3, add.smooth=FALSE, which=1)
E<-resid(Zip4)
hist(E, xlab="Residuals", main="")
plot(a$t.amb, E, xlab="Temperature", ylab="residuals")
plot(a$h.amb, E, xlab="Humidity", ylab="residuals")
plot(a$phase, E, xlab="Phase", ylab="residuals")
plot(a$hour, E, xlab="Hour", ylab="residuals")
plot(a$total, E, xlab="total", ylab="residuals")
# The residuals are a bit more overdispersed than before, but because of the nature of the data I think it is more appropiate to include the colony Id as a random factor.

# Adding colony ID as a random factor to the zero inflated model with negative binomial distribution
Zip5<- glmmadmb (inds~t.amb+h.amb+phase+total+hour+ (1|colony), data = a, zeroInflation = TRUE, family = "nbinom")
summary(Zip5)

op<-par(mfrow=c(2,2), mar=c(5,4,1,2))
#plot(Zip3, add.smooth=FALSE, which=1)
E<-resid(Zip5)
hist(E, xlab="Residuals", main="")
plot(a$t.amb, E, xlab="Temperature", ylab="residuals")
plot(a$h.amb, E, xlab="Humidity", ylab="residuals")
plot(a$phase, E, xlab="Phase", ylab="residuals")
plot(a$hour, E, xlab="Hour", ylab="residuals")
plot(a$total, E, xlab="total", ylab="residuals")


#Final model
summary(Zip5)

```


## Analizing feeding data
```{r}
a<-datajune%>% filter(beh=="A")
ggplot(a, aes(x=hour, y=prop)) +geom_bar(stat="identity") + facet_wrap(~location)

ggplot(a, aes(x=daytime, y=prop)) +geom_point(stat="identity") + facet_wrap(~location, nrow=3)

#ggplot(data=a, aes(x=daytime,y=prop))+
 # geom_density_ridges(stat="identity", jittered_points=T, scale=0.8)+
  #theme_classic()

mod1<-glm(inds~t.amb+h.amb+phase+hour2+total, family = poisson, data =a)
summary(mod1)
sum.mod1 <- glance(mod1)
sum.mod1
gof.p.mod1 <- with(sum.mod1,pchisq(deviance,df.residual,lower=FALSE))
gof.p.mod1

# Checking assumptions
mod1.test <- augment(mod1)
lin.vor <- ggplot(mod1.test, aes(x = t.amb, y = .std.resid)) + geom_count() + 
  scale_size_area(max_size=4) + 
  geom_hline(yintercept = 0, linetype = 2) + 
  geom_smooth() + guides(size = FALSE)
lin.pc1 <- lin.vor + aes(x = h.amb)
lin.pc2 <- lin.vor + aes(x = phase)
lin.pc3 <- lin.vor + aes(x = hour2)
grid.arrange(lin.vor, lin.pc1, lin.pc2, lin.pc3)
# all seems to be within the acceptable range (do not differ from 0)
# Checking residual plots:
resd1 <- ggplot(mod1.test, aes(x = .fitted, y = .resid)) + 
  geom_point() + 
  geom_smooth() + 
  geom_hline(yintercept = 0, linetype=2) 

resd2 <- resd1 + aes(y = sqrt(abs(.std.resid))) +
  geom_hline(yintercept = 1, linetype=2)

resd3 <- ggplot(mod1.test, aes(.hat, .std.resid)) +
 geom_vline(size = 2, colour = "white", xintercept = 0) +
  geom_hline(size = 2, colour = "white", yintercept = 0) +
  geom_point(aes(size = .cooksd)) + geom_smooth(se = FALSE) 

# get int and slope for qqline
probs <- c(0.25,0.75)
y <- quantile(mod1.test$.std.resid, probs, names = FALSE, na.rm = TRUE)
x <- qnorm(probs)
slope <- diff(y)/diff(x)
int <- y[1L] - slope * x[1L]

qq.mod <- ggplot(mod1.test, aes(sample=.std.resid)) + 
  geom_qq(size=rel(4)) + 
  geom_abline(intercept = int, slope = slope, linetype = 2, size = 2) 

grid.arrange(resd1, resd2, resd3, qq.mod)

# The residuals look overdispersed

# trying adding a random factor to the poisson distribution
mod2<-glmmPQL(inds~t.amb+h.amb+phase+hour2, random=~1|total, family = poisson, data =a)
summary(mod2)

op<-par(mfrow=c(2,2), mar=c(5,4,1,2))
plot(mod2, add.smooth=FALSE, which=1)
E<-resid(mod2)
hist(E, xlab="Residuals", main="")
plot(a$t.amb, E, xlab="Temperature", ylab="residuals")
plot(a$h.amb, E, xlab="Humidity", ylab="residuals")
plot(a$phase, E, xlab="Phase", ylab="residuals")
plot(a$hour2, E, xlab="Hour", ylab="residuals")

# The residuals do not look good.

#Trying negavitve binomial distribution
mod3<-glm.nb(inds~t.amb+h.amb+phase+hour+total, data =a)
summary(mod3)

op<-par(mfrow=c(2,2), mar=c(5,4,1,2))
plot(mod3, add.smooth=FALSE, which=1)
E<-resid(mod2)
hist(E, xlab="Residuals", main="")
plot(a$t.amb, E, xlab="Temperature", ylab="residuals")
plot(a$h.amb, E, xlab="Humidity", ylab="residuals")
plot(a$phase, E, xlab="Phase", ylab="residuals")
plot(a$hour2, E, xlab="Hour", ylab="residuals")
 
# The residuals do not look good.

#Trying adding a random factor with a negative binomial distribution
mod4<-glmmPQL(inds~t.amb+h.amb+phase+hour2, data=a, random = ~ 1 | total, family = negative.binomial (theta =  0.671, link = log))
summary(mod4)

op<-par(mfrow=c(2,2), mar=c(5,4,1,2))
plot(mod4, add.smooth=FALSE, which=1)
E<-resid(mod4)
hist(E, xlab="Residuals", main="")
plot(a$t.amb, E, xlab="Temperature", ylab="residuals")
plot(a$h.amb, E, xlab="Humidity", ylab="residuals")
plot(a$phase, E, xlab="Phase", ylab="residuals")
plot(a$hour2, E, xlab="Hour", ylab="residuals")

# The residuals do not look good.

# Trying a zero inflated analysis with Poisson distribution
Zip1<-zeroinfl(inds~t.amb+phase+hour+total|t.amb+phase+hour+total, dist= "poisson", link = "logit", data=a)
summary(Zip1)

mnull <- update(Zip1, . ~ 1)
summary(mnull)
pchisq(2 * (logLik(Zip1) - logLik(mnull)), df = 3, lower.tail = FALSE)

op<-par(mfrow=c(2,2), mar=c(5,4,1,2))
#plot(Zip1, add.smooth=FALSE, which=1)
E<-resid(Zip1)
hist(E, xlab="Residuals", main="")
plot(a$t.amb, E, xlab="Temperature", ylab="residuals")
plot(a$h.amb, E, xlab="Humidity", ylab="residuals")
plot(a$phase, E, xlab="Phase", ylab="residuals")
plot(a$hour, E, xlab="Hour", ylab="residuals")
plot(a$total, E, xlab="Total", ylab="residuals")

# The residulas look closer to zero and less overdispersed, lets try a zero inflated with a negative binomial distribution
Zip3<-zeroinfl(inds~t.amb+h.amb+phase+total+hour|t.amb+h.amb+phase+total+hour, dist= "negbin", link = "logit", data=a)
summary(Zip3)

op<-par(mfrow=c(2,2), mar=c(5,4,1,2))
#plot(Zip3, add.smooth=FALSE, which=1)
E<-resid(Zip3)
hist(E, xlab="Residuals", main="")
plot(a$t.amb, E, xlab="Temperature", ylab="residuals")
plot(a$h.amb, E, xlab="Humidity", ylab="residuals")
plot(a$phase, E, xlab="Phase", ylab="residuals")
plot(a$hour, E, xlab="Hour", ylab="residuals")
plot(a$total, E, xlab="total", ylab="residuals")

# The residuals are a bit less overdispersed than before, I think this one works best

#Final model
summary(Zip3)

```

## Analizing peeking out
```{r}
a<-datajune%>% filter(beh=="S")
ggplot(a, aes(x=hour, y=prop)) +geom_bar(stat="identity") + facet_wrap(~location)

ggplot(a, aes(x=daytime, y=prop)) +geom_point(stat="identity") + facet_wrap(~location, nrow=3)

#ggplot(data=a, aes(x=daytime,y=prop))+
 # geom_density_ridges(stat="identity", jittered_points=T, scale=0.8)+
  #theme_classic()

mod1<-glm(inds~t.amb+h.amb+phase+hour2+total, family = poisson, data =a)
summary(mod1)
sum.mod1 <- glance(mod1)
sum.mod1
gof.p.mod1 <- with(sum.mod1,pchisq(deviance,df.residual,lower=FALSE))
gof.p.mod1

# Checking assumptions
mod1.test <- augment(mod1)
lin.vor <- ggplot(mod1.test, aes(x = t.amb, y = .std.resid)) + geom_count() + 
  scale_size_area(max_size=4) + 
  geom_hline(yintercept = 0, linetype = 2) + 
  geom_smooth() + guides(size = FALSE)
lin.pc1 <- lin.vor + aes(x = h.amb)
lin.pc2 <- lin.vor + aes(x = phase)
lin.pc3 <- lin.vor + aes(x = hour2)
grid.arrange(lin.vor, lin.pc1, lin.pc2, lin.pc3)
# all seems to be within the acceptable range (do not differ from 0)
# Checking residual plots:
resd1 <- ggplot(mod1.test, aes(x = .fitted, y = .resid)) + 
  geom_point() + 
  geom_smooth() + 
  geom_hline(yintercept = 0, linetype=2) 

resd2 <- resd1 + aes(y = sqrt(abs(.std.resid))) +
  geom_hline(yintercept = 1, linetype=2)

resd3 <- ggplot(mod1.test, aes(.hat, .std.resid)) +
 geom_vline(size = 2, colour = "white", xintercept = 0) +
  geom_hline(size = 2, colour = "white", yintercept = 0) +
  geom_point(aes(size = .cooksd)) + geom_smooth(se = FALSE) 

# get int and slope for qqline
probs <- c(0.25,0.75)
y <- quantile(mod1.test$.std.resid, probs, names = FALSE, na.rm = TRUE)
x <- qnorm(probs)
slope <- diff(y)/diff(x)
int <- y[1L] - slope * x[1L]

qq.mod <- ggplot(mod1.test, aes(sample=.std.resid)) + 
  geom_qq(size=rel(4)) + 
  geom_abline(intercept = int, slope = slope, linetype = 2, size = 2) 

grid.arrange(resd1, resd2, resd3, qq.mod)

# The residuals look overdispersed

# trying adding a random factor to the poisson distribution
mod2<-glmmPQL(inds~t.amb+h.amb+phase+hour2, random=~1|total, family = poisson, data =a)
summary(mod2)

op<-par(mfrow=c(2,2), mar=c(5,4,1,2))
plot(mod2, add.smooth=FALSE, which=1)
E<-resid(mod2)
hist(E, xlab="Residuals", main="")
plot(a$t.amb, E, xlab="Temperature", ylab="residuals")
plot(a$h.amb, E, xlab="Humidity", ylab="residuals")
plot(a$phase, E, xlab="Phase", ylab="residuals")
plot(a$hour2, E, xlab="Hour", ylab="residuals")

# The residuals do not look good.

#Trying negavitve binomial distribution
mod3<-glm.nb(inds~t.amb+h.amb+phase+hour+total, data =a)
summary(mod3)

op<-par(mfrow=c(2,2), mar=c(5,4,1,2))
plot(mod3, add.smooth=FALSE, which=1)
E<-resid(mod2)
hist(E, xlab="Residuals", main="")
plot(a$t.amb, E, xlab="Temperature", ylab="residuals")
plot(a$h.amb, E, xlab="Humidity", ylab="residuals")
plot(a$phase, E, xlab="Phase", ylab="residuals")
plot(a$hour2, E, xlab="Hour", ylab="residuals")
 
# The residuals do not look good.

#Trying adding a random factor with a negative binomial distribution
mod4<-glmmPQL(inds~t.amb+h.amb+phase+hour2, data=a, random = ~ 1 | total, family = negative.binomial (theta =  0.671, link = log))
summary(mod4)

op<-par(mfrow=c(2,2), mar=c(5,4,1,2))
plot(mod4, add.smooth=FALSE, which=1)
E<-resid(mod4)
hist(E, xlab="Residuals", main="")
plot(a$t.amb, E, xlab="Temperature", ylab="residuals")
plot(a$h.amb, E, xlab="Humidity", ylab="residuals")
plot(a$phase, E, xlab="Phase", ylab="residuals")
plot(a$hour2, E, xlab="Hour", ylab="residuals")

# The residuals do not look good.

# Trying a zero inflated analysis with Poisson distribution
Zip1<-zeroinfl(inds~t.amb+phase+hour+total|t.amb+phase+hour+total, dist= "poisson", link = "logit", data=a)
summary(Zip1)

mnull <- update(Zip1, . ~ 1)
summary(mnull)
pchisq(2 * (logLik(Zip1) - logLik(mnull)), df = 3, lower.tail = FALSE)

op<-par(mfrow=c(2,2), mar=c(5,4,1,2))
#plot(Zip1, add.smooth=FALSE, which=1)
E<-resid(Zip1)
hist(E, xlab="Residuals", main="")
plot(a$t.amb, E, xlab="Temperature", ylab="residuals")
plot(a$h.amb, E, xlab="Humidity", ylab="residuals")
plot(a$phase, E, xlab="Phase", ylab="residuals")
plot(a$hour, E, xlab="Hour", ylab="residuals")
plot(a$total, E, xlab="Total", ylab="residuals")

# The residulas look closer to zero and less overdispersed, lets try a zero inflated with a negative binomial distribution
Zip3<-zeroinfl(inds~t.amb+h.amb+phase+total+hour|t.amb+h.amb+phase+total+hour, dist= "negbin", link = "logit", data=a)
summary(Zip3)

op<-par(mfrow=c(2,2), mar=c(5,4,1,2))
#plot(Zip3, add.smooth=FALSE, which=1)
E<-resid(Zip3)
hist(E, xlab="Residuals", main="")
plot(a$t.amb, E, xlab="Temperature", ylab="residuals")
plot(a$h.amb, E, xlab="Humidity", ylab="residuals")
plot(a$phase, E, xlab="Phase", ylab="residuals")
plot(a$hour, E, xlab="Hour", ylab="residuals")
plot(a$total, E, xlab="total", ylab="residuals")

# The residuals are a bit less overdispersed than before, I think this one works best

#Final model
summary(Zip3)

```

## Analizing hiding
```{r}
a<-datajune%>% filter(beh=="E")
ggplot(a, aes(x=hour, y=prop)) +geom_bar(stat="identity") + facet_wrap(~location)

ggplot(a, aes(x=daytime, y=prop)) +geom_point(stat="identity") + facet_wrap(~location, nrow=3)

#ggplot(data=a, aes(x=daytime,y=prop))+
 # geom_density_ridges(stat="identity", jittered_points=T, scale=0.8)+
  #theme_classic()

mod1<-glm(inds~t.amb+h.amb+phase+hour2+total, family = poisson, data =a)
summary(mod1)
sum.mod1 <- glance(mod1)
sum.mod1
gof.p.mod1 <- with(sum.mod1,pchisq(deviance,df.residual,lower=FALSE))
gof.p.mod1

# Checking assumptions
mod1.test <- augment(mod1)
lin.vor <- ggplot(mod1.test, aes(x = t.amb, y = .std.resid)) + geom_count() + 
  scale_size_area(max_size=4) + 
  geom_hline(yintercept = 0, linetype = 2) + 
  geom_smooth() + guides(size = FALSE)
lin.pc1 <- lin.vor + aes(x = h.amb)
lin.pc2 <- lin.vor + aes(x = phase)
lin.pc3 <- lin.vor + aes(x = hour2)
grid.arrange(lin.vor, lin.pc1, lin.pc2, lin.pc3)
# all seems to be within the acceptable range (do not differ from 0)
# Checking residual plots:
resd1 <- ggplot(mod1.test, aes(x = .fitted, y = .resid)) + 
  geom_point() + 
  geom_smooth() + 
  geom_hline(yintercept = 0, linetype=2) 

resd2 <- resd1 + aes(y = sqrt(abs(.std.resid))) +
  geom_hline(yintercept = 1, linetype=2)

resd3 <- ggplot(mod1.test, aes(.hat, .std.resid)) +
 geom_vline(size = 2, colour = "white", xintercept = 0) +
  geom_hline(size = 2, colour = "white", yintercept = 0) +
  geom_point(aes(size = .cooksd)) + geom_smooth(se = FALSE) 

# get int and slope for qqline
probs <- c(0.25,0.75)
y <- quantile(mod1.test$.std.resid, probs, names = FALSE, na.rm = TRUE)
x <- qnorm(probs)
slope <- diff(y)/diff(x)
int <- y[1L] - slope * x[1L]

qq.mod <- ggplot(mod1.test, aes(sample=.std.resid)) + 
  geom_qq(size=rel(4)) + 
  geom_abline(intercept = int, slope = slope, linetype = 2, size = 2) 

grid.arrange(resd1, resd2, resd3, qq.mod)

# The residuals look overdispersed

# trying adding a random factor to the poisson distribution
mod2<-glmmPQL(inds~t.amb+h.amb+phase+hour2, random=~1|total, family = poisson, data =a)
summary(mod2)

op<-par(mfrow=c(2,2), mar=c(5,4,1,2))
plot(mod2, add.smooth=FALSE, which=1)
E<-resid(mod2)
hist(E, xlab="Residuals", main="")
plot(a$t.amb, E, xlab="Temperature", ylab="residuals")
plot(a$h.amb, E, xlab="Humidity", ylab="residuals")
plot(a$phase, E, xlab="Phase", ylab="residuals")
plot(a$hour2, E, xlab="Hour", ylab="residuals")

# The residuals do not look good.

#Trying negavitve binomial distribution
mod3<-glm.nb(inds~t.amb+h.amb+phase+hour+total, data =a)
summary(mod3)

op<-par(mfrow=c(2,2), mar=c(5,4,1,2))
plot(mod3, add.smooth=FALSE, which=1)
E<-resid(mod2)
hist(E, xlab="Residuals", main="")
plot(a$t.amb, E, xlab="Temperature", ylab="residuals")
plot(a$h.amb, E, xlab="Humidity", ylab="residuals")
plot(a$phase, E, xlab="Phase", ylab="residuals")
plot(a$hour2, E, xlab="Hour", ylab="residuals")
 
# The residuals do not look good.

#Trying adding a random factor with a negative binomial distribution
mod4<-glmmPQL(inds~t.amb+h.amb+phase+hour, data=a, random = ~ 1 | total, family = negative.binomial (theta =  0.671, link = log))
summary(mod4)

op<-par(mfrow=c(2,2), mar=c(5,4,1,2))
plot(mod4, add.smooth=FALSE, which=1)
E<-resid(mod4)
hist(E, xlab="Residuals", main="")
plot(a$t.amb, E, xlab="Temperature", ylab="residuals")
plot(a$h.amb, E, xlab="Humidity", ylab="residuals")
plot(a$phase, E, xlab="Phase", ylab="residuals")
plot(a$hour2, E, xlab="Hour", ylab="residuals")

# The residuals do not look too bad

# Trying a zero inflated analysis with Poisson distribution
Zip1<-zeroinfl(inds~t.amb+phase+hour+total|t.amb+phase+hour+total, dist= "poisson", link = "logit", data=a)
summary(Zip1)

mnull <- update(Zip1, . ~ 1)
summary(mnull)
pchisq(2 * (logLik(Zip1) - logLik(mnull)), df = 3, lower.tail = FALSE)

op<-par(mfrow=c(2,2), mar=c(5,4,1,2))
#plot(Zip1, add.smooth=FALSE, which=1)
E<-resid(Zip1)
hist(E, xlab="Residuals", main="")
plot(a$t.amb, E, xlab="Temperature", ylab="residuals")
plot(a$h.amb, E, xlab="Humidity", ylab="residuals")
plot(a$phase, E, xlab="Phase", ylab="residuals")
plot(a$hour, E, xlab="Hour", ylab="residuals")
plot(a$total, E, xlab="Total", ylab="residuals")

# The residulas look closer to zero and less overdispersed, lets try a zero inflated with a negative binomial distribution
Zip3<-zeroinfl(inds~t.amb+h.amb+phase+total+hour|t.amb+h.amb+phase+total+hour, dist= "negbin", link = "logit", data=a)
summary(Zip3)

op<-par(mfrow=c(2,2), mar=c(5,4,1,2))
#plot(Zip3, add.smooth=FALSE, which=1)
E<-resid(Zip3)
hist(E, xlab="Residuals", main="")
plot(a$t.amb, E, xlab="Temperature", ylab="residuals")
plot(a$h.amb, E, xlab="Humidity", ylab="residuals")
plot(a$phase, E, xlab="Phase", ylab="residuals")
plot(a$hour, E, xlab="Hour", ylab="residuals")
plot(a$total, E, xlab="total", ylab="residuals")

# The residuals are a bit less overdispersed than before, I think this one works best

#Final model
summary(mod4)

```


## Analizing outside
```{r}
a<-datajune%>% filter(beh=="F")
ggplot(a, aes(x=hour, y=prop)) +geom_bar(stat="identity") + facet_wrap(~location)

ggplot(a, aes(x=daytime, y=prop)) +geom_point(stat="identity") + facet_wrap(~location, nrow=3)

#ggplot(data=a, aes(x=daytime,y=prop))+
 # geom_density_ridges(stat="identity", jittered_points=T, scale=0.8)+
  #theme_classic()

mod1<-glm(inds~t.amb+h.amb+phase+hour2+total, family = poisson, data =a)
summary(mod1)
sum.mod1 <- glance(mod1)
sum.mod1
gof.p.mod1 <- with(sum.mod1,pchisq(deviance,df.residual,lower=FALSE))
gof.p.mod1

# Checking assumptions
mod1.test <- augment(mod1)
lin.vor <- ggplot(mod1.test, aes(x = t.amb, y = .std.resid)) + geom_count() + 
  scale_size_area(max_size=4) + 
  geom_hline(yintercept = 0, linetype = 2) + 
  geom_smooth() + guides(size = FALSE)
lin.pc1 <- lin.vor + aes(x = h.amb)
lin.pc2 <- lin.vor + aes(x = phase)
lin.pc3 <- lin.vor + aes(x = hour2)
grid.arrange(lin.vor, lin.pc1, lin.pc2, lin.pc3)
# all seems to be within the acceptable range (do not differ from 0)
# Checking residual plots:
resd1 <- ggplot(mod1.test, aes(x = .fitted, y = .resid)) + 
  geom_point() + 
  geom_smooth() + 
  geom_hline(yintercept = 0, linetype=2) 

resd2 <- resd1 + aes(y = sqrt(abs(.std.resid))) +
  geom_hline(yintercept = 1, linetype=2)

resd3 <- ggplot(mod1.test, aes(.hat, .std.resid)) +
 geom_vline(size = 2, colour = "white", xintercept = 0) +
  geom_hline(size = 2, colour = "white", yintercept = 0) +
  geom_point(aes(size = .cooksd)) + geom_smooth(se = FALSE) 

# get int and slope for qqline
probs <- c(0.25,0.75)
y <- quantile(mod1.test$.std.resid, probs, names = FALSE, na.rm = TRUE)
x <- qnorm(probs)
slope <- diff(y)/diff(x)
int <- y[1L] - slope * x[1L]

qq.mod <- ggplot(mod1.test, aes(sample=.std.resid)) + 
  geom_qq(size=rel(4)) + 
  geom_abline(intercept = int, slope = slope, linetype = 2, size = 2) 

grid.arrange(resd1, resd2, resd3, qq.mod)

# The residuals look overdispersed

# trying adding a random factor to the poisson distribution
mod2<-glmmPQL(inds~t.amb+h.amb+phase+hour2, random=~1|total, family = poisson, data =a)
summary(mod2)

op<-par(mfrow=c(2,2), mar=c(5,4,1,2))
plot(mod2, add.smooth=FALSE, which=1)
E<-resid(mod2)
hist(E, xlab="Residuals", main="")
plot(a$t.amb, E, xlab="Temperature", ylab="residuals")
plot(a$h.amb, E, xlab="Humidity", ylab="residuals")
plot(a$phase, E, xlab="Phase", ylab="residuals")
plot(a$hour2, E, xlab="Hour", ylab="residuals")

# The residuals do not look good.

#Trying negavitve binomial distribution
mod3<-glm.nb(inds~t.amb+h.amb+phase+hour+total, data =a)
summary(mod3)

op<-par(mfrow=c(2,2), mar=c(5,4,1,2))
plot(mod3, add.smooth=FALSE, which=1)
E<-resid(mod2)
hist(E, xlab="Residuals", main="")
plot(a$t.amb, E, xlab="Temperature", ylab="residuals")
plot(a$h.amb, E, xlab="Humidity", ylab="residuals")
plot(a$phase, E, xlab="Phase", ylab="residuals")
plot(a$hour2, E, xlab="Hour", ylab="residuals")
 
# The residuals do not look good.

#Trying adding a random factor with a negative binomial distribution
mod4<-glmmPQL(inds~t.amb+h.amb+phase+hour, data=a, random = ~ 1 | total, family = negative.binomial (theta =  0.671, link = log))
summary(mod4)

op<-par(mfrow=c(2,2), mar=c(5,4,1,2))
plot(mod4, add.smooth=FALSE, which=1)
E<-resid(mod4)
hist(E, xlab="Residuals", main="")
plot(a$t.amb, E, xlab="Temperature", ylab="residuals")
plot(a$h.amb, E, xlab="Humidity", ylab="residuals")
plot(a$phase, E, xlab="Phase", ylab="residuals")
plot(a$hour2, E, xlab="Hour", ylab="residuals")

# The residuals do not look too bad

# Trying a zero inflated analysis with Poisson distribution
Zip1<-zeroinfl(inds~t.amb+phase+hour+total|t.amb+phase+hour+total, dist= "poisson", link = "logit", data=a)
summary(Zip1)

mnull <- update(Zip1, . ~ 1)
summary(mnull)
pchisq(2 * (logLik(Zip1) - logLik(mnull)), df = 3, lower.tail = FALSE)

op<-par(mfrow=c(2,2), mar=c(5,4,1,2))
#plot(Zip1, add.smooth=FALSE, which=1)
E<-resid(Zip1)
hist(E, xlab="Residuals", main="")
plot(a$t.amb, E, xlab="Temperature", ylab="residuals")
plot(a$h.amb, E, xlab="Humidity", ylab="residuals")
plot(a$phase, E, xlab="Phase", ylab="residuals")
plot(a$hour, E, xlab="Hour", ylab="residuals")
plot(a$total, E, xlab="Total", ylab="residuals")

# The residulas look closer to zero and less overdispersed, lets try a zero inflated with a negative binomial distribution
Zip3<-zeroinfl(inds~t.amb+h.amb+phase+total+hour|t.amb+h.amb+phase+total+hour, dist= "negbin", link = "logit", data=a)
summary(Zip3)

op<-par(mfrow=c(2,2), mar=c(5,4,1,2))
#plot(Zip3, add.smooth=FALSE, which=1)
E<-resid(Zip3)
hist(E, xlab="Residuals", main="")
plot(a$t.amb, E, xlab="Temperature", ylab="residuals")
plot(a$h.amb, E, xlab="Humidity", ylab="residuals")
plot(a$phase, E, xlab="Phase", ylab="residuals")
plot(a$hour, E, xlab="Hour", ylab="residuals")
plot(a$total, E, xlab="total", ylab="residuals")

# The residuals are a bit less overdispersed than before, I think this one works best

#Final model
summary(Zip3)

```

# Plotting 
```{r}
# Temperature
datajune$t2<-as.factor(round(datajune$t.amb))

ggplot(data=datajune, aes(x=t2, y=prop)) +geom_boxplot()+ facet_wrap(~beh2) +theme_classic() + ylab("Proportion")+
  xlab("Temperature (°C)")

datajune %>% group_by(beh2, t2) %>%
  summarize(mean=mean(prop), stdev=sd(prop)) %>% ggplot(aes(x=t2, y=mean, group=1)) +
  geom_line()+ 
  geom_point() + 
  facet_wrap(~beh2) + 
  geom_errorbar(aes(ymin=mean-stdev,
                    ymax=mean+stdev),
                width = 0.2) +
  theme_classic() +
  ylab("Mean proportion")+
  xlab("Temperature (°C)")

ggplot(data=datajune, aes(x=t2, y=inds)) +geom_boxplot()+ facet_wrap(~beh2) +theme_classic() + ylab("Proportion")+
  xlab("Temperature (°C)")


datajune %>% group_by(beh2, t2) %>%
  summarize(mean=mean(inds), stdev=sd(inds)) %>% ggplot(aes(x=t2, y=mean, group=1)) +
  geom_line()+ 
  geom_point() + 
  facet_wrap(~beh2) + 
  geom_errorbar(aes(ymin=mean-stdev,
                    ymax=mean+stdev),
                width = 0.2) +
  theme_classic() +
  ylab("Mean proportion")+
  xlab("Temperature (°C)")

# Humidity
datajune$h2<-as.factor(round(datajune$h.amb))


ggplot(data=datajune, aes(x=h2, y=inds)) +geom_boxplot()+ facet_wrap(~beh2) +theme_classic() + ylab("Proportion")+
  xlab("Humidity (%)")


datajune %>% group_by(beh2, h2) %>%
  summarize(mean=mean(inds), stdev=sd(inds)) %>% ggplot(aes(x=h2, y=mean, group=1)) +
  geom_line()+ 
  geom_point() + 
  facet_wrap(~beh2) + 
  geom_errorbar(aes(ymin=mean-stdev,
                    ymax=mean+stdev),
                width = 0.2) +
  theme_classic() +
  ylab("Mean proportion")+
  xlab("Temperature (°C)")

# Hour
ggplot(data=datajune, aes(x=hour2, y=inds)) +geom_boxplot()+ facet_wrap(~beh2) +theme_classic() + ylab("Proportion")+
  xlab("Hour")


datajune %>% group_by(beh2, hour2) %>%
  summarize(mean=mean(inds), stdev=sd(inds)) %>% ggplot(aes(x=hour2, y=mean, group=1)) +
  geom_line()+ 
  geom_point() + 
  facet_wrap(~beh2) + 
  geom_errorbar(aes(ymin=mean-stdev,
                    ymax=mean+stdev),
                width = 0.2) +
  theme_classic() +
  ylab("Mean proportion")+
  xlab("Temperature (°C)")

# Phase
ggplot(data=datajune, aes(x=phase, y=inds)) +geom_boxplot()+ facet_wrap(~beh2) +theme_classic() + ylab("Proportion")+
  xlab("Lunar phase")


datajune %>% group_by(beh2, phase) %>%
  summarize(mean=mean(inds), stdev=sd(inds)) %>% ggplot(aes(x=phase, y=mean, group=1)) +
  geom_line()+ 
  geom_point() + 
  facet_wrap(~beh2) + 
  geom_errorbar(aes(ymin=mean-stdev,
                    ymax=mean+stdev),
                width = 0.2) +
  theme_classic() +
  ylab("Mean proportion")+
  xlab("Temperature (°C)")

```




# Looking at the activity scale for the two months

## How does activity vary with hour (time)?

### For all data
```{r}


#All data
ggplot(data=data2, aes(x=daytime,y=act4))+
  geom_boxplot()+
  geom_jitter(aes(color=location))+
  theme_classic()

ggplot(data=data2, aes(y=daytime,x=act4))+
  geom_boxplot()+
  geom_jitter(aes(color=location))+
  theme_classic()


ggplot(data=data2, aes(x=daytime))+
  geom_histogram()+
 facet_wrap(~act4)+
  theme_classic()

data2%>%ggplot(aes(x=hour2, fill=act4))+geom_bar(position = position_fill(reverse = TRUE)) + scale_fill_brewer(palette="Reds" ) + ylab("Proportion") + xlab("Hour")+theme_classic() +guides(fill=guide_legend(title="Activity scale")) + facet_wrap(~location, nrow=3)

ggsave("Plots/activityscale_all.png", plot = last_plot(), width=6, heigh=4, units="in")


data2%>%ggplot(aes(x=hour2, fill=act4))+geom_bar(position = position_fill(reverse = TRUE)) + scale_fill_brewer(palette="Reds" ) + ylab("Proportion") + xlab("Hour")+theme_classic() +guides(fill=guide_legend(title="Activity scale")) + facet_wrap(~colony)

ggsave("Plots/activityscale_colony.png", plot = last_plot(), width=6, heigh=4, units="in")

ggplot(data=data2, aes(x=daytime,y=act4))+
  geom_density_ridges( jittered_points=T, scale=0.8)+
  theme_classic()
```

### Only BCI
```{r}

data2%>%filter(location=="BCI") %>%
  ggplot(aes(x=daytime, y=act4))+
  geom_boxplot() +
  geom_jitter()+
  theme_classic()

data2%>%filter(location=="BCI") %>%
  ggplot(aes(x=daytime))+
  geom_histogram()+
 facet_wrap(~act4)+
  theme_classic()

data2%>%filter(location=="BCI") %>%
  ggplot(aes(x=hour, fill=act4))+
  geom_histogram()

data2%>%filter(location=="BCI") %>% ggplot(aes(x=hour2, fill=act4))+geom_bar(position = position_fill(reverse = TRUE)) + scale_fill_brewer(palette="Reds" ) + ylab("Proportion") + xlab("Hour")+theme_classic() +guides(fill=guide_legend(title="Activity scale"))


data2%>%filter(location=="BCI") %>%
ggplot(aes(x=daytime,y=act4))+
  geom_density_ridges( jittered_points=T, scale=0.8)+
  theme_classic()
```
## How does activity vary between locations?

```{r}
#All data
ggplot(data=data2, aes(x=location,y=act3))+
  geom_boxplot()+
  geom_jitter(aes(color=daytime))+
  theme_classic()

ggplot(data2, aes(x=location, fill=act4)) +geom_bar(position = position_fill(reverse = TRUE)) + scale_fill_brewer(palette="Reds" ) + ylab("Proportion") + xlab("Location")+theme_classic() +guides(fill=guide_legend(title="Activity scale"))
ggsave("Plots/activityscale_locations.png", plot = last_plot(), width=6, heigh=4, units="in")


# Using an ordinal logistic regresion
model<-polr(act4~location, data=data2, Hess=T)
summary(model)
## store table
(ctable <- coef(summary(model)))

## calculate and store p values
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2

## combined table
(ctable <- cbind(ctable, "p value" = p))


#Plotting the effects 
library("effects")
Effect(focal.predictors = "location",model)
plot(Effect(focal.predictors = "location",model))



```

## How does activity vary between colonies?

```{r}
#All data
ggplot(data=data2, aes(x=colony,y=act3))+
  geom_boxplot()+
  geom_jitter(aes(color=daytime))+
  theme_classic()

ggplot(data2, aes(x=colony, fill=act4)) +geom_bar(position = position_fill(reverse = TRUE)) + scale_fill_brewer(palette="Reds" ) + ylab("Proportion") + xlab("Colony")+theme_classic() +guides(fill=guide_legend(title="Activity scale"))
ggsave("Plots/activityscale_colony.png", plot = last_plot(), width=6, heigh=4, units="in")


# Using an ordinal logistic regresion
model<-polr(act4~colony, data=data2, Hess=T)
summary(model)
## store table
(ctable <- coef(summary(model)))

## calculate and store p values
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2

## combined table
(ctable <- cbind(ctable, "p value" = p))


#Plotting the effects 
library("effects")
Effect(focal.predictors = "colony",model)
plot(Effect(focal.predictors = "colony",model))



```



## How does activity vary with all the environmental factors? (global model)

```{r}
# Using an ordinal logistic regresion
m<-polr(act4~t.amb+h.amb+phase+hour, data=data2, Hess=T) #Ojo: temperature y humedad estan correlacionadas, mejor hacer solo 1. Ademas aca no incluye el efecto de la colonia
summary(m)
## store table
(ctable <- coef(summary(m)))
## calculate and store p values
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
## combined table
(ctable <- cbind(ctable, "p value" = p))

#Plotting the effects 
library("effects")
Effect(focal.predictors ="t.amb", m)
plot(Effect(focal.predictors = "t.amb",m))
Effect(focal.predictors ="h.amb", m)
plot(Effect(focal.predictors = "h.amb",m))
Effect(focal.predictors ="phase", m)
plot(Effect(focal.predictors = "phase",m))

# Adding colony as a random factor
m2<-clmm(act4~t.amb+phase+hour+(1|colony), data=data2, Hess=T)
summary(m2)

m3<-clmm(act4~h.amb+phase+hour+(1|colony), data=data2, Hess=T)
summary(m3)


m4<-clmm(act4~t.amb+h.amb+phase+hour+(1|colony), data=data2, Hess=T)
summary(m4)


# checking which variables contribute more to the model
models <- list(act4~1+(1|colony),
              act4~t.amb+(1|colony),
              act4~h.amb+(1|colony),
              act4~hour+(1|colony),
              act4~phase+(1|colony),
              act4~t.amb+h.amb+(1|colony),
               act4~t.amb+hour+(1|colony),
               act4~t.amb+phase+(1|colony),
               act4~h.amb+hour+(1|colony),
               act4~h.amb+phase+(1|colony),
               act4~hour+phase+(1|colony),
              act4~t.amb+h.amb+hour+(1|colony),
              act4~t.amb+h.amb+phase+(1|colony),
              act4~t.amb+hour+phase+(1|colony),
              act4~h.amb+hour+phase+(1|colony),
              act4~t.amb+h.amb+hour+phase+(1|colony))

fits <- map(models, clmm, data=data2)
aic <- map_dbl(fits,AIC)
aic
which.min(aic)
models[[which.min(aic)]] 

m5<-clmm(act4~t.amb+hour+(1|colony), data=data2, Hess=T)
summary(m5)

```


## Plot: How does activity vary with ambient temperature?
```{r}
#All data
ggplot(data=data2, aes(x=round(t.amb),y=act4))+
  geom_boxplot()+
  geom_jitter(aes(color=location))+
  theme_classic()

ggplot(data=data2, aes(x=t.amb,y=act4))+
  geom_density_ridges( jittered_points=T, scale=0.8)+
  theme_classic()

min(data2$t.amb)
max(data2$t.amb)

data2$rt.amb<-round(data2$t.amb)
dat<-data2 %>% group_by(rt.amb, act4) %>% summarize(n=n())
dat%>% ggplot(aes(x=rt.amb, y=n, fill=act4))+geom_bar(position = position_fill(reverse = TRUE), stat="identity") + scale_fill_brewer(palette="Reds" ) + ylab("Proportion") + xlab("Temperature (°C)")+theme_classic() +guides(fill=guide_legend(title="Activity scale"))


data2%>% ggplot(aes(x=round(t.amb), fill=act4))+geom_bar(position = position_fill(reverse = TRUE)) + scale_fill_brewer(palette="Reds" ) + ylab("Proportion") + xlab("Temperature (°C)")+theme_classic() +guides(fill=guide_legend(title="Activity scale"))

ggsave("Plots/activityscale_temperature.png", plot = last_plot(), width=6, heigh=4, units="in")

data2%>% ggplot(aes(x=round(t.amb), fill=act4))+geom_bar(position = position_fill(reverse = TRUE)) + scale_fill_brewer(palette="Reds" ) + ylab("Proportion") + xlab("Temperature (°C)")+theme_classic() +guides(fill=guide_legend(title="Activity scale")) +facet_wrap(~colony)
ggsave("Plots/activityscale_temperatureby colony.png", plot = last_plot(), width=6, heigh=4, units="in")

data2%>% ggplot(aes(x=round(t.amb), fill=act4))+geom_bar(position = position_fill(reverse = TRUE)) + scale_fill_brewer(palette="Reds" ) + ylab("Proportion") + xlab("Temperature (°C)")+theme_classic() +guides(fill=guide_legend(title="Activity scale")) +facet_wrap(~location)
ggsave("Plots/activityscale_temperaturebylocation.png", plot = last_plot(), width=6, heigh=4, units="in")


ggplot(data=data2, aes(x=t.amb))+
  geom_histogram(binwidth=1)+
 facet_wrap(~act4)+
  theme_classic()

data2%>% ggplot(aes(y=round(t.amb), x=act4))+geom_boxplot() + ylab("Activity scale") + xlab("Temperature (°C)")+theme_classic() + geom_jitter()



```
## Plot: How does activity vary with ambient humidity?
```{r}
#All data
ggplot(data=data2, aes(x=h.amb,y=act4))+
  geom_boxplot()+
  geom_jitter(aes(color=location))+
  theme_classic()

ggplot(data=data2, aes(x=h.amb,y=act4))+
  geom_density_ridges( jittered_points=T, scale=0.8)+
  theme_classic()

data2<-data2 %>% mutate(rh.amb=case_when(between(h.amb, 80,85)~"80-85",
                                  between(h.amb, 85,90)~"85-90", 
                                  between(h.amb, 90,95)~"90-95",
                                  between(h.amb, 95,100)~"95-100", 
                                  TRUE~NA))

data2%>% ggplot(aes(x=rh.amb, fill=act4))+geom_bar(position = position_fill(reverse = TRUE)) + scale_fill_brewer(palette="Reds" ) + ylab("Proportion") + xlab("Humidity (%)")+theme_classic() +guides(fill=guide_legend(title="Activity scale")) 
ggsave("Plots/activityscale_humidity.png", plot = last_plot(), width=6, heigh=4, units="in")

data2%>% ggplot(aes(x=rh.amb, fill=act4))+geom_bar(position = position_fill(reverse = TRUE)) + scale_fill_brewer(palette="Reds" ) + ylab("Proportion") + xlab("Humidity (%)")+theme_classic() +guides(fill=guide_legend(title="Activity scale")) +facet_wrap(~colony)
ggsave("Plots/activityscale_humiditybycolony.png", plot = last_plot(), width=6, heigh=4, units="in")


data2%>% ggplot(aes(x=h.amb, y=act3,color=act))+geom_line() + geom_point()+ scale_color_brewer(palette="Reds" ) + ylab("Activity") + xlab("Humidity (%)")+theme_classic() +guides(fill=guide_legend(title="Activity scale"))
ggsave("Plots/activityscale_humidity2.png", plot = last_plot(), width=6, heigh=4, units="in")



```


## Plot: How does activity vary with lunar phase?
```{r}
#All data
ggplot(data=data2, aes(x=phase,y=act2))+
  geom_boxplot()+
  geom_jitter(aes(color=location))+
  theme_classic()

ggplot(data=data2, aes(x=act2,y=phase))+
  geom_density_ridges(jittered_points=T, scale=0.8)+
  theme_classic()

data2%>% ggplot(aes(x=phase, fill=act4))+geom_bar(position = position_fill(reverse = TRUE)) + scale_fill_brewer(palette="Reds" ) + ylab("Proportion") + xlab("Lunar phase")+theme_classic() +guides(fill=guide_legend(title="Activity scale"))
ggsave("Plots/activityscale_phase.png", plot = last_plot(), width=6, heigh=4, units="in")

data2%>% ggplot(aes(x=phase, fill=act4))+geom_bar(position = position_fill(reverse = TRUE)) + scale_fill_brewer(palette="Reds" ) + ylab("Proportion") + xlab("Lunar phase")+theme_classic() +guides(fill=guide_legend(title="Activity scale"))+facet_wrap(~colony)
ggsave("Plots/activityscale_phasebycolony.png", plot = last_plot(), width=6, heigh=4, units="in")
```



